---
title: "A Continuation of Reassessment: Minimum Wage's Impact on Income Inequality"
bibliography: citations.bib
  
author: 
  - name: "Donald Young"
    affiliations:
        - name: "California State Polytechnic University, Pomona"
          department: "Department of Economics"
format:
  pdf:
    documentclass: report
    template-partials:
      - "latex/before-body.tex"
    include-in-header:
      - "latex/preamble.tex"
      - text: |
          \usepackage{booktabs}
          \usepackage{pdflscape}
          \usepackage{float}
          \usepackage{caption}
          \captionsetup{labelformat=empty}
    toc: false
    lof: false
    lot: false


filters: 
  - first-line-indent

editor: source


abstract: |
  Abstract: 
  Since the seminal work of @lee1999wage, scholars have debated the extent to which the federal minimum wage drives lower-tail wage inequality in the United States. This paper extends the analysis of @autor2016minimum, which serves as a reassessment of Lee's findings using data through 2012, by incorporating an additional twelve years of CPS Merged Outgoing Rotation Group data through 2024. This period is of particular interest because the real value of the average minimum wage has increased substantially since 2012, providing new identifying variation. Replicating the instrument variables strategy of @autor2016minimum, I find that the minimum wage's contribution to lower-tail inequality is modestly smaller than even the revised estimates of that study, consistent with the hypothesis that broad state-level minimum wage increases have compressed the lower-tail of the wage distribution while leaving upper-tail inequality largely unaffected.
---

```{r,echo=FALSE,message=FALSE,warning=FALSE}
# =============================================================================
# R Code to Reproduce Stata .gph Figures
# Figures: fig1a, fig1b, fig7 (×4 periods), fig10a, fig10b, fig10c
# Generated from parsed Stata serset binary data
# =============================================================================

library(ggplot2)
library(scales)

# ── Shared theme (mimics Stata's stcolor scheme) ─────────────────────────────
stata_theme <- theme_bw() +
  theme(
    panel.background  = element_rect(fill = "white", color = "white"),
    plot.background   = element_rect(fill = "white", color = "white"),
    panel.border      = element_rect(color = "grey80"),
    panel.grid.major  = element_line(color = "white", linewidth = 0.4),
    panel.grid.minor  = element_blank(),
    legend.background = element_rect(fill = "white", color = NA),
    legend.key        = element_rect(fill = "white"),
    legend.position   = "bottom",
    legend.text       = element_text(size = 7),
    axis.text         = element_text(size = 7),
    axis.title        = element_text(size = 7),
    plot.margin       = margin(4, 6, 4, 6, "pt")
  )

# =============================================================================
# DATA
# =============================================================================

# ── fig1a data ────────────────────────────────────────────────────────────────
fig1a <- data.frame(
  year       = 1979:2024,
  realmin    = c(2.216376, 2.156418, 2.135780, 2.076010, 2.044410, 2.002151, 1.967308, 1.950325, 1.916114, 1.895206, 1.871074, 1.917551, 1.970977, 1.948416, 1.919266, 1.897516, 1.869522, 1.842963, 1.929964, 1.997783, 1.981767, 1.956492, 1.944338, 1.941686, 1.922724, 1.900728, 1.895947, 1.891463, 1.956944, 1.978015, 2.033784, 2.061588, 2.033918, 2.008201, 1.997410, 2.011223, 2.029642, 2.043711, 2.050970, 2.060195, 2.107910, 2.107107, 2.112243, 2.077897, 2.098879, 2.102287),
  realfedmin = c(2.216058, 2.156129, 2.135513, 2.075730, 2.044111, 2.001844, 1.966852, 1.948435, 1.912589, 1.872049, 1.824991, 1.898409, 1.969107, 1.939448, 1.909952, 1.884669, 1.856723, 1.827623, 1.916163, 1.981559, 1.959713, 1.926653, 1.898595, 1.882908, 1.860373, 1.834092, 1.800772, 1.769024, 1.740940, 1.830708, 1.947295, 2.032562, 2.001485, 1.981001, 1.966460, 1.950368, 1.949182, 1.936646, 1.915566, 1.891435, 1.873477, 1.861216, 1.815306, 1.738320, 1.697980, 1.668912),
  lp1050f    = c(-0.382208, -0.421465, -0.400478, -0.495788, -0.530628, -0.538997, -0.579818, -0.603101, -0.624154, -0.615761, -0.628609, -0.632523, -0.600057, -0.599621, -0.598610, -0.587787, -0.604316, -0.653921, -0.616186, -0.562939, -0.600438, -0.591336, -0.613104, -0.598576, -0.605131, -0.619039, -0.656780, -0.658056, -0.652325, -0.628609, -0.634123, -0.636577, -0.652687, -0.693147, -0.693166, -0.682485, -0.682800, -0.661450, -0.678798, -0.641854, -0.653626, -0.673060, -0.657520, -0.628609, -0.632523, -0.610748),
  lp1050m    = c(-0.667829, -0.678963, -0.680075, -0.693147, -0.733969, -0.782759, -0.750306, -0.767074, -0.773190, -0.744440, -0.693147, -0.721735, -0.762140, -0.788457, -0.739667, -0.730618, -0.721390, -0.693147, -0.733969, -0.693147, -0.681653, -0.706051, -0.693147, -0.693147, -0.696170, -0.693147, -0.699378, -0.743528, -0.708326, -0.693147, -0.720546, -0.710837, -0.711496, -0.781460, -0.759278, -0.748237, -0.744440, -0.702714, -0.741937, -0.722918, -0.711110, -0.733969, -0.693147, -0.637976, -0.645223, -0.654060)
)

# ── fig1b data ────────────────────────────────────────────────────────────────
fig1b <- data.frame(
  year       = 1979:2024,
  realmin    = fig1a$realmin,
  realfedmin = fig1a$realfedmin,
  lp9050f    = c(0.593302, 0.587199, 0.647685, 0.613341, 0.643492, 0.653482, 0.672944, 0.655202, 0.665996, 0.678259, 0.693147, 0.693147, 0.721699, 0.726208, 0.725206, 0.759279, 0.766285, 0.757684, 0.741937, 0.788953, 0.756792, 0.759538, 0.759282, 0.775414, 0.773195, 0.797022, 0.797299, 0.794930, 0.800104, 0.808074, 0.830732, 0.838327, 0.844275, 0.825271, 0.842186, 0.856661, 0.851483, 0.859200, 0.843720, 0.863819, 0.856282, 0.832617, 0.823816, 0.836246, 0.837847, 0.843167),
  lp9050m    = c(0.584934, 0.579818, 0.611623, 0.628609, 0.652325, 0.664160, 0.680725, 0.658738, 0.678944, 0.693147, 0.693147, 0.742678, 0.732229, 0.737599, 0.768567, 0.764089, 0.746548, 0.771698, 0.767252, 0.779197, 0.770778, 0.790059, 0.802342, 0.836243, 0.828775, 0.818798, 0.843187, 0.826688, 0.821065, 0.828278, 0.843429, 0.862231, 0.858716, 0.864402, 0.875177, 0.883499, 0.877066, 0.867502, 0.850258, 0.856552, 0.840756, 0.836035, 0.836246, 0.797026, 0.822718, 0.914556)
)

# ── fig7 data (b4_marg, ub4_marg, lb4_marg vs percentile p) ──────────────────
fig7_1979_1989 <- data.frame(
  p        = 5:95,
  b4_marg  = c(3.903602, 2.132766, 0.869642, 1.150032, -1.357991, -1.141460, 0.670412, 0.344580, 0.058018, 0.296021, -0.491633, -0.687132, -0.192570, -2.425344, -2.336969, 0.010891, 0.455827, 0.146090, 0.474658, 0.649737, 0.171879, -1.336325, -0.704310, 0.517130, 0.013594, -0.912500, -1.178143, -0.368627, -0.386577, -0.545062, -0.025858, -0.145068, -0.391305, -0.322168, -0.475402, -1.998302, -1.623806, -0.778135, -0.802810, -1.839623, -1.645420, -2.123816, -2.016731, -1.554564, -0.782111, 0.000000, -0.012279, -1.106543, -1.598464, -2.032779, -1.993086, -1.532542, -1.209144, -1.850014, -2.296807, -1.925311, -1.073738, -1.377582, -0.991514, -0.040013, -0.874995, -0.475122, -0.841026, -0.738313, -1.017097, -1.478933, -0.766305, -0.963925, -1.345696, -0.723700, -0.529567, -0.967189, -1.040681, -0.667639, 0.151740, -0.841842, -0.890611, -0.041728, -0.946645, -0.458590, -0.627288, -0.986008, -1.386136, -0.819870, 0.039280, -0.869170, -1.377322, -0.973331, -1.519764, -1.847111, -0.276127),
  ub4_marg = c(26.792854, 13.939728, 5.737020, 7.254627, 12.218958, 10.792017, 3.650743, 2.778112, 2.789005, 2.726556, 6.537974, 8.014231, 5.393496, 19.336536, 18.765388, 3.677012, 2.305908, 2.628197, 2.724439, 4.016755, 3.083618, 12.467729, 8.296884, 2.366489, 3.033782, 8.827029, 10.361443, 5.315472, 6.068141, 7.646395, 3.696926, 2.936187, 4.491565, 5.142261, 5.713935, 15.001315, 12.760387, 7.687777, 7.097085, 13.120684, 11.770440, 15.263287, 14.844690, 11.552438, 6.254108, 0.000000, 0.781354, 7.782337, 11.610003, 14.778969, 14.670135, 11.941135, 9.293921, 13.537033, 16.322908, 14.095493, 8.883825, 10.524700, 7.958527, 2.070544, 6.514496, 4.476983, 6.819769, 7.037519, 9.092238, 11.975469, 7.662436, 9.538031, 11.327418, 7.387023, 5.707584, 9.003925, 9.177410, 6.698089, 2.743167, 8.293201, 8.829441, 4.389989, 9.676470, 6.509492, 7.838983, 10.734301, 12.552958, 8.251211, 2.907012, 8.408627, 11.299306, 9.101868, 12.849498, 14.641143, 4.324863),
  lb4_marg = c(-18.985651, -9.674196, -3.997736, -4.954564, -14.934940, -13.074937, -2.309919, -2.088952, -2.672968, -2.134514, -7.521240, -9.388494, -5.778636, -24.187225, -23.439327, -3.655231, -1.394254, -2.336017, -1.775124, -2.717281, -2.739860, -15.140378, -9.705504, -1.332229, -3.006594, -10.652028, -12.717729, -6.052725, -6.841296, -8.736518, -3.748641, -3.226323, -5.274175, -5.786597, -6.664738, -18.997919, -16.007999, -9.244048, -8.702706, -16.799931, -15.061280, -19.510918, -18.878153, -14.661566, -7.818329, 0.000000, -0.805911, -9.995423, -14.806932, -18.844526, -18.656307, -15.006220, -11.712210, -17.237061, -20.916523, -17.946115, -11.031301, -13.279863, -9.941554, -2.150570, -8.264486, -5.427227, -8.501822, -8.514144, -11.126433, -14.933334, -9.195046, -11.465880, -14.018810, -8.834424, -6.766719, -10.938303, -11.258773, -8.033367, -2.439687, -9.976885, -10.610662, -4.473444, -11.569760, -7.426672, -9.093558, -12.706316, -15.325230, -9.890952, -2.828451, -10.146967, -14.053950, -11.048530, -15.889026, -18.335365, -4.877116)
)

fig7_1979_1991 <- data.frame(
  p        = 5:95,
  b4_marg  = c(0.536237, 0.473970, 0.373654, 0.288084, 0.332349, 0.440516, 0.417510, 0.289301, 0.101644, 0.033057, 0.034350, 0.103937, 0.142040, 0.199081, 0.241874, 0.193621, 0.091926, 0.116905, 0.033886, 0.114407, 0.146830, 0.122602, 0.111542, 0.121391, 0.119289, 0.100074, 0.073747, 0.078173, 0.142745, 0.114722, 0.092365, 0.077770, 0.041943, 0.008064, 0.029336, 0.075510, 0.067870, 0.114201, 0.044526, 0.061255, 0.053403, 0.123786, 0.187624, 0.121582, 0.073637, 0.000000, 0.001899, 0.010560, -0.003194, 0.050886, 0.018078, 0.050722, 0.053022, 0.036689, 0.084262, 0.088973, 0.033558, 0.048460, 0.006651, -0.022329, -0.040921, 0.005504, -0.020598, -0.029827, -0.003851, 0.033955, 0.058037, 0.095042, 0.076375, 0.047679, 0.041478, 0.087168, 0.069580, 0.053109, 0.091347, 0.095227, 0.059315, 0.086851, 0.076519, 0.095278, 0.124375, 0.129783, 0.128313, 0.060548, 0.064464, 0.015605, 0.042900, 0.045702, 0.064247, 0.042058, -0.136512),
  ub4_marg = c(0.648842, 0.599053, 0.497924, 0.395525, 0.418975, 0.521789, 0.520261, 0.365820, 0.192275, 0.168085, 0.157304, 0.204340, 0.222434, 0.266898, 0.319609, 0.262824, 0.155181, 0.194125, 0.134640, 0.206734, 0.225866, 0.192398, 0.176914, 0.177666, 0.168901, 0.155472, 0.142095, 0.160906, 0.219303, 0.185513, 0.153097, 0.150615, 0.116194, 0.073746, 0.109612, 0.156110, 0.123320, 0.179982, 0.095878, 0.110592, 0.114604, 0.214857, 0.310563, 0.190590, 0.136988, 0.000000, 0.031515, 0.057892, 0.050404, 0.123307, 0.079575, 0.122958, 0.119557, 0.099431, 0.169717, 0.157944, 0.106052, 0.158175, 0.076386, 0.029682, 0.017886, 0.055117, 0.031772, 0.038538, 0.057254, 0.111680, 0.144854, 0.178205, 0.159498, 0.143859, 0.128375, 0.177666, 0.148708, 0.129574, 0.171047, 0.184700, 0.137552, 0.182562, 0.148153, 0.199911, 0.251716, 0.242281, 0.232113, 0.143585, 0.156948, 0.087018, 0.115760, 0.137442, 0.170893, 0.153849, -0.027903),
  lb4_marg = c(0.423633, 0.348887, 0.249384, 0.180643, 0.245723, 0.359242, 0.314759, 0.212782, 0.011013, -0.101970, -0.088604, 0.003535, 0.061645, 0.131263, 0.164140, 0.124418, 0.028670, 0.039685, -0.066867, 0.022079, 0.067795, 0.052806, 0.046169, 0.065117, 0.069677, 0.044677, 0.005400, -0.004559, 0.066187, 0.043931, 0.031633, 0.004924, -0.032308, -0.057619, -0.050939, -0.005091, 0.012420, 0.048420, -0.006827, 0.011918, -0.007799, 0.032715, 0.064686, 0.052574, 0.010285, 0.000000, -0.027716, -0.036773, -0.056792, -0.021535, -0.043418, -0.021514, -0.013512, -0.026054, -0.001193, 0.020003, -0.038936, -0.061255, -0.063085, -0.074340, -0.099729, -0.044109, -0.072968, -0.098191, -0.064956, -0.043770, -0.028780, 0.011880, -0.006748, -0.048501, -0.045418, -0.003329, -0.009547, -0.023356, 0.011647, 0.005754, -0.018923, -0.008859, 0.004886, -0.009356, -0.002967, 0.017285, 0.024514, -0.022488, -0.028019, -0.055807, -0.029960, -0.046038, -0.042399, -0.069732, -0.245121)
)

fig7_1979_2012 <- data.frame(
  p        = 5:95,
  b4_marg  = c(0.276160, 0.246370, 0.170274, 0.154978, 0.150449, 0.145963, 0.116032, 0.081776, 0.077068, 0.042210, 0.027426, 0.039411, 0.049410, 0.061686, 0.051860, 0.050089, 0.032152, 0.020979, -0.003815, 0.016141, 0.002192, -0.022794, 0.012080, 0.023710, 0.003271, 0.019198, 0.016292, 0.039916, 0.020905, 0.006703, 0.002802, -0.005823, -0.014437, -0.007154, 0.016883, 0.017711, 0.020627, 0.013085, 0.032082, 0.032090, 0.012505, 0.020716, 0.030523, 0.006177, 0.007862, 0.000000, -0.020297, 0.001033, 0.001310, 0.013808, 0.000674, 0.008531, 0.007616, 0.002257, 0.000082, -0.005323, -0.025261, -0.034640, -0.015486, -0.030930, -0.022807, -0.009685, -0.011779, -0.002564, -0.006100, -0.004362, 0.001227, 0.017612, 0.002563, 0.014628, -0.003186, 0.022321, 0.012034, 0.011173, 0.013060, 0.008051, 0.008854, 0.014826, 0.017777, 0.027905, 0.013783, 0.012761, 0.020326, 0.003227, -0.002200, -0.004287, 0.017249, 0.039946, 0.034580, 0.018453, -0.010654),
  ub4_marg = c(0.348336, 0.307975, 0.227743, 0.232126, 0.207345, 0.188211, 0.162935, 0.139723, 0.152794, 0.140853, 0.128569, 0.116203, 0.121542, 0.121956, 0.086090, 0.084137, 0.073126, 0.060981, 0.039726, 0.050539, 0.045682, 0.033171, 0.058066, 0.063289, 0.056863, 0.062760, 0.052999, 0.073653, 0.060234, 0.037634, 0.039081, 0.029476, 0.025955, 0.029147, 0.042062, 0.041544, 0.038450, 0.034959, 0.061235, 0.054833, 0.030703, 0.043522, 0.056746, 0.022054, 0.028554, 0.000000, 0.006939, 0.018001, 0.025338, 0.035021, 0.021235, 0.031074, 0.036064, 0.025407, 0.030042, 0.024052, 0.000743, -0.004600, 0.008391, -0.007554, 0.001823, 0.015972, 0.014249, 0.032354, 0.023033, 0.028064, 0.031757, 0.054861, 0.040046, 0.054828, 0.041648, 0.065155, 0.055107, 0.050363, 0.063476, 0.052907, 0.052180, 0.059603, 0.062222, 0.082278, 0.074241, 0.066231, 0.072027, 0.057703, 0.057287, 0.068321, 0.077863, 0.103184, 0.099056, 0.085739, 0.078676),
  lb4_marg = c(0.203984, 0.184765, 0.112804, 0.077829, 0.093553, 0.103714, 0.069128, 0.023829, 0.001342, -0.056432, -0.073717, -0.037381, -0.022722, 0.001416, 0.017630, 0.016041, -0.008823, -0.019024, -0.047357, -0.018257, -0.041297, -0.078758, -0.033907, -0.015869, -0.050320, -0.024363, -0.020415, 0.006178, -0.018424, -0.024227, -0.033478, -0.041122, -0.054830, -0.043456, -0.008297, -0.006122, 0.002803, -0.008789, 0.002929, 0.009348, -0.005693, -0.002090, 0.004301, -0.009699, -0.012829, 0.000000, -0.047533, -0.015936, -0.022717, -0.007404, -0.019888, -0.014011, -0.020832, -0.020893, -0.029878, -0.034697, -0.051264, -0.064680, -0.039364, -0.054306, -0.047436, -0.035343, -0.037807, -0.037482, -0.035232, -0.036787, -0.029304, -0.019637, -0.034921, -0.025571, -0.048020, -0.020514, -0.031040, -0.028016, -0.037356, -0.036804, -0.034472, -0.029950, -0.026669, -0.026467, -0.046674, -0.040709, -0.031375, -0.051248, -0.061688, -0.076895, -0.043364, -0.023292, -0.029896, -0.048833, -0.099984)
)

fig7_1979_2024 <- data.frame(
  p        = 5:95,
  b4_marg  = c(0.197804, 0.216479, 0.236255, 0.236619, 0.245629, 0.233043, 0.210666, 0.195925, 0.193196, 0.171771, 0.161731, 0.150753, 0.146552, 0.154258, 0.140621, 0.132685, 0.116945, 0.101283, 0.091457, 0.092238, 0.090142, 0.066638, 0.060835, 0.070013, 0.065165, 0.065790, 0.051209, 0.055803, 0.044396, 0.043556, 0.040738, 0.033988, 0.032669, 0.032173, 0.037025, 0.038023, 0.023608, 0.021383, 0.026274, 0.019028, 0.009331, 0.013042, 0.014276, 0.007743, 0.006588, 0.000000, -0.000478, 0.010975, 0.003475, 0.013641, 0.010093, 0.005909, 0.007430, 0.000608, -0.000975, -0.003440, -0.011275, -0.000990, -0.005882, -0.010632, -0.004845, -0.005790, -0.007608, -0.004225, -0.012048, -0.014536, -0.018137, -0.015508, -0.015842, -0.016343, -0.027758, -0.019451, -0.020853, -0.023565, -0.025150, -0.022454, -0.030660, -0.038096, -0.043007, -0.036625, -0.031255, -0.027510, -0.020783, -0.037642, -0.033914, -0.026069, -0.011819, 0.010175, 0.016978, 0.031123, 0.059110),
  ub4_marg = c(0.249818, 0.268090, 0.292156, 0.295739, 0.312363, 0.312429, 0.284480, 0.272720, 0.278743, 0.244456, 0.228505, 0.218566, 0.223010, 0.232226, 0.227783, 0.220039, 0.198004, 0.177220, 0.163134, 0.166481, 0.161044, 0.126123, 0.123716, 0.136753, 0.125157, 0.120148, 0.101568, 0.106918, 0.088433, 0.084324, 0.081627, 0.064414, 0.061034, 0.064062, 0.079037, 0.082837, 0.055729, 0.045120, 0.059065, 0.043861, 0.031514, 0.034124, 0.032856, 0.020042, 0.019775, 0.000000, 0.004777, 0.021835, 0.013308, 0.025782, 0.027248, 0.016303, 0.019869, 0.014239, 0.014945, 0.011698, 0.004929, 0.012295, 0.012791, 0.008876, 0.017939, 0.018501, 0.017104, 0.019883, 0.011919, 0.008660, 0.005839, 0.011970, 0.010625, 0.010370, -0.000868, 0.009253, 0.004672, 0.006810, 0.003143, 0.008910, 0.001320, -0.002060, -0.008921, -0.001872, 0.002972, 0.012969, 0.021707, 0.003806, 0.015118, 0.024212, 0.049426, 0.069836, 0.068562, 0.094623, 0.123823),
  lb4_marg = c(0.145789, 0.164868, 0.180355, 0.177499, 0.178895, 0.153658, 0.136852, 0.119131, 0.107649, 0.099086, 0.094956, 0.082941, 0.070095, 0.076290, 0.053460, 0.045331, 0.035885, 0.025347, 0.019781, 0.017994, 0.019241, 0.007153, -0.002046, 0.003274, 0.005173, 0.011431, 0.000851, 0.004688, 0.000359, 0.002787, -0.000150, 0.003562, 0.004304, 0.000285, -0.004986, -0.006791, -0.008512, -0.002353, -0.006517, -0.005804, -0.012851, -0.008039, -0.004303, -0.004556, -0.006600, 0.000000, -0.005733, 0.000116, -0.006357, 0.001500, -0.007062, -0.004485, -0.005009, -0.013022, -0.016894, -0.018578, -0.027478, -0.014275, -0.024555, -0.030141, -0.027629, -0.030081, -0.032320, -0.028333, -0.036014, -0.037731, -0.042113, -0.042987, -0.042310, -0.043057, -0.054648, -0.048156, -0.046379, -0.053939, -0.053443, -0.053818, -0.062640, -0.074132, -0.077092, -0.071377, -0.065482, -0.067989, -0.063272, -0.079089, -0.082946, -0.076349, -0.073063, -0.049487, -0.034607, -0.032377, -0.005602)
)

# ── fig10 data ────────────────────────────────────────────────────────────────
fig10a <- data.frame(
  year     = 1979:2024,
  me_lvl   = c(0.100758, 0.097943, 0.096338, 0.085846, 0.080300, 0.074086, 0.068211, 0.062145, 0.057268, 0.053805, 0.050079, 0.058192, 0.064612, 0.061635, 0.057433, 0.054712, 0.052151, 0.045792, 0.056092, 0.062057, 0.056699, 0.051411, 0.046462, 0.043042, 0.038904, 0.036056, 0.036193, 0.035863, 0.044301, 0.046851, 0.050680, 0.056356, 0.054312, 0.051361, 0.049446, 0.048365, 0.051132, 0.050594, 0.048983, 0.050362, 0.051902, 0.040778, 0.044432, 0.041374, 0.042069, 0.040013),
  spiketl  = c(0.042513, 0.046946, 0.048013, 0.037324, 0.035535, 0.029939, 0.026246, 0.022647, 0.019767, 0.018263, 0.014039, 0.013167, 0.029030, 0.022869, 0.018636, 0.013609, 0.012206, 0.012584, 0.017544, 0.015866, 0.012610, 0.010302, 0.008481, 0.007834, 0.005543, 0.005667, 0.006993, 0.011270, 0.011617, 0.013619, 0.020559, 0.018268, 0.017366, 0.015998, 0.013376, 0.002783, 0.016359, 0.018269, 0.016362, 0.015144, 0.015953, 0.009837, 0.011967, 0.007583, 0.008847, 0.011548),
  spiketu  = c(0.086436, 0.091472, 0.094634, 0.086871, 0.077334, 0.071997, 0.066677, 0.063928, 0.060689, 0.056915, 0.052669, 0.053069, 0.068959, 0.061346, 0.056675, 0.051113, 0.049740, 0.049167, 0.053437, 0.052585, 0.048063, 0.046488, 0.044157, 0.044484, 0.049292, 0.050744, 0.051103, 0.056754, 0.057994, 0.058136, 0.066789, 0.065139, 0.063946, 0.032593, 0.063148, 0.051261, 0.063929, 0.065729, 0.062492, 0.059817, 0.059803, 0.045669, 0.050192, 0.045472, 0.047406, 0.049633)
)

fig10b <- data.frame(
  year     = 1979:2024,
  me_lvl   = c(0.031639, 0.030860, 0.030619, 0.027892, 0.026433, 0.024650, 0.022983, 0.021406, 0.020352, 0.020070, 0.019587, 0.022761, 0.025836, 0.025503, 0.024257, 0.023732, 0.022517, 0.021305, 0.024853, 0.026567, 0.024515, 0.023300, 0.021607, 0.020995, 0.020038, 0.019203, 0.019596, 0.019303, 0.022194, 0.023099, 0.024572, 0.027039, 0.027257, 0.024962, 0.024817, 0.025114, 0.025091, 0.025130, 0.024986, 0.024968, 0.025539, 0.021899, 0.023794, 0.022946, 0.023083, 0.022072),
  spiketl  = c(0.035484, 0.040914, 0.040223, 0.033202, 0.032151, 0.027855, 0.024217, 0.020346, 0.017689, 0.017230, 0.013309, 0.011921, 0.029462, 0.022360, 0.018658, 0.012806, 0.010816, 0.010557, 0.018037, 0.014867, 0.011466, 0.009883, 0.007961, 0.007584, 0.005433, 0.005568, 0.006485, 0.006860, 0.010923, 0.013721, 0.021012, 0.017577, 0.017510, 0.013722, 0.011166, 0.003342, 0.011927, 0.016683, 0.012078, 0.010708, 0.012852, 0.009381, 0.008508, 0.005677, 0.007361, 0.009184),
  spiketu  = c(0.079407, 0.085439, 0.086844, 0.082749, 0.073950, 0.069914, 0.064648, 0.061627, 0.058612, 0.055883, 0.051938, 0.051823, 0.069390, 0.060837, 0.056698, 0.050311, 0.048351, 0.047140, 0.053930, 0.051586, 0.046919, 0.046070, 0.043637, 0.044233, 0.049182, 0.050645, 0.050596, 0.052345, 0.057300, 0.058238, 0.067242, 0.064448, 0.064090, 0.030317, 0.060938, 0.051820, 0.059497, 0.064144, 0.058208, 0.055381, 0.056703, 0.045213, 0.046733, 0.043565, 0.045920, 0.047269)
)

fig10c <- data.frame(
  year     = 1979:2024,
  me_lvl   = c(0.073811, 0.072012, 0.071454, 0.064240, 0.060107, 0.054995, 0.050112, 0.045376, 0.041151, 0.039979, 0.038261, 0.046489, 0.052634, 0.050974, 0.047892, 0.045482, 0.041736, 0.038826, 0.047891, 0.053056, 0.047671, 0.043570, 0.039509, 0.038036, 0.034845, 0.031860, 0.032382, 0.032327, 0.039368, 0.041364, 0.045139, 0.050952, 0.050498, 0.046504, 0.045480, 0.045641, 0.046275, 0.046207, 0.045339, 0.045633, 0.047048, 0.038019, 0.042732, 0.039624, 0.039464, 0.037725),
  spiketl  = c(0.042472, 0.047979, 0.049703, 0.038882, 0.036452, 0.030093, 0.026264, 0.022109, 0.019311, 0.018529, 0.014250, 0.017643, 0.029974, 0.023491, 0.019328, 0.013489, 0.011722, 0.014564, 0.017839, 0.015681, 0.012034, 0.015263, 0.008374, 0.007849, 0.005508, 0.005760, 0.006683, 0.007120, 0.011260, 0.016139, 0.021099, 0.018074, 0.017510, 0.014650, 0.012242, 0.003598, 0.014107, 0.020750, 0.016629, 0.012826, 0.016396, 0.009621, 0.009991, 0.007015, 0.008041, 0.010324),
  spiketu  = c(0.086395, 0.092505, 0.096324, 0.088430, 0.078251, 0.072151, 0.066694, 0.063390, 0.060234, 0.057181, 0.052879, 0.057544, 0.069903, 0.061968, 0.057367, 0.050994, 0.049256, 0.051147, 0.053732, 0.052400, 0.047488, 0.051450, 0.044051, 0.044499, 0.049257, 0.050836, 0.050793, 0.052605, 0.057637, 0.060657, 0.067329, 0.064944, 0.064090, 0.031245, 0.062015, 0.052076, 0.061677, 0.068211, 0.062759, 0.057500, 0.060247, 0.045453, 0.048217, 0.044903, 0.046600, 0.048409)
)


# =============================================================================
# FIGURE 1a
# Minimum wage & bottom wage percentiles (1979–2024)
# Left axis:  Log real minimum wage, 2012 dollars
# Right axis: Log(p10) - log(p50)
# =============================================================================

# Dual-axis scaling: map right-axis range onto left-axis range
la_lo <- 1.6;  la_hi <- 2.2   # left-axis limits
ra_lo <- -0.8; ra_hi <- -0.2  # right-axis limits

scale_to_left <- function(x) (x - ra_lo) / (ra_hi - ra_lo) * (la_hi - la_lo) + la_lo
unscale_left  <- function(x) (x - la_lo) / (la_hi - la_lo) * (ra_hi - ra_lo) + ra_lo

fig1a_plot <- ggplot(fig1a, aes(x = year)) +
  # Left-axis series
  geom_line(aes(y = realmin,    color = "Avg. real value of state/fed. mins (L axis)",
                linetype = "Avg. real value of state/fed. mins (L axis)"), linewidth = 0.7) +
  geom_line(aes(y = realfedmin, color = "Real value of fed. min. (L axis)",
                linetype = "Real value of fed. min. (L axis)"), linewidth = 0.9) +
  # Right-axis series scaled to left axis
  geom_line(aes(y = scale_to_left(lp1050f),
                color = "log(p10)-log(p50), female (R axis)",
                linetype = "log(p10)-log(p50), female (R axis)"), linewidth = 0.7) +
  geom_point(aes(y = scale_to_left(lp1050f),
                 color = "log(p10)-log(p50), female (R axis)"), shape = 1, size = 1.5) +
  geom_line(aes(y = scale_to_left(lp1050m),
                color = "log(p10)-log(p50), male (R axis)",
                linetype = "log(p10)-log(p50), male (R axis)"), linewidth = 0.7) +
  geom_point(aes(y = scale_to_left(lp1050m),
                 color = "log(p10)-log(p50), male (R axis)"), shape = 2, size = 1.5) +
  # Left axis
  scale_y_continuous(
    name   = "Log real minimum wage, 2012 dollars",
    limits = c(la_lo, la_hi),
    breaks = seq(1.6, 2.2, 0.1),
    labels = number_format(accuracy = 0.1),
    # Secondary (right) axis
    sec.axis = sec_axis(
      transform = unscale_left,
      name   = "Log(p10)\u2013log(p50)",
      breaks = seq(-0.8, -0.2, 0.1),
      labels = number_format(accuracy = 0.1)
    )
  ) +
  scale_x_continuous(
    breaks = c(1974, 1980, 1985, 1990, 1995, 2000, 2005, 2010, 2015, 2020, 2024),
    limits = c(1974, 2025)
  ) +
  scale_color_manual(
    name = NULL,
    values = c(
      "Avg. real value of state/fed. mins (L axis)" = "#1F3E6E",  # navy
      "Real value of fed. min. (L axis)"            = "#8B1A1A",  # maroon
      "log(p10)-log(p50), female (R axis)"          = "#228B22",  # forest green
      "log(p10)-log(p50), male (R axis)"            = "#D46A00"   # dkorange
    )
  ) +
  scale_linetype_manual(
    name = NULL,
    values = c(
      "Avg. real value of state/fed. mins (L axis)" = "dashed",
      "Real value of fed. min. (L axis)"            = "dotted",
      "log(p10)-log(p50), female (R axis)"          = "solid",
      "log(p10)-log(p50), male (R axis)"            = "solid"
    )
  ) +
  guides(
    color    = guide_legend(nrow = 2),
    linetype = guide_legend(nrow = 2)
  ) +
  labs(x = NULL) +
  stata_theme +
  theme(
    legend.position  = "bottom",
    legend.margin    = margin(0, 0, 0, 0),
    axis.title.y     = element_text(size = 7),
    axis.title.y.right = element_text(size = 7)
  )


# =============================================================================
# FIGURE 1b
# Minimum wage & top wage percentiles (1979–2024)
# Left axis:  Log real minimum wage, 2012 dollars
# Right axis: Log(p90) - log(p50)
# =============================================================================

ra_lo_b <- 0.5; ra_hi_b <- 1.1

scale_to_left_b <- function(x) (x - ra_lo_b) / (ra_hi_b - ra_lo_b) * (la_hi - la_lo) + la_lo
unscale_left_b  <- function(x) (x - la_lo) / (la_hi - la_lo) * (ra_hi_b - ra_lo_b) + ra_lo_b

fig1b_plot <- ggplot(fig1b, aes(x = year)) +
  geom_line(aes(y = realmin,    color = "Avg. real value of state/fed. mins (L axis)",
                linetype = "Avg. real value of state/fed. mins (L axis)"), linewidth = 0.7) +
  geom_line(aes(y = realfedmin, color = "Real value of fed. min. (L axis)",
                linetype = "Real value of fed. min. (L axis)"), linewidth = 0.9) +
  geom_line(aes(y = scale_to_left_b(lp9050f),
                color = "log(p90)-log(p50), female (R axis)",
                linetype = "log(p90)-log(p50), female (R axis)"), linewidth = 0.7) +
  geom_point(aes(y = scale_to_left_b(lp9050f),
                 color = "log(p90)-log(p50), female (R axis)"), shape = 1, size = 1.5) +
  geom_line(aes(y = scale_to_left_b(lp9050m),
                color = "log(p90)-log(p50), male (R axis)",
                linetype = "log(p90)-log(p50), male (R axis)"), linewidth = 0.7) +
  geom_point(aes(y = scale_to_left_b(lp9050m),
                 color = "log(p90)-log(p50), male (R axis)"), shape = 2, size = 1.5) +
  scale_y_continuous(
    name   = "Log real minimum wage, 2012 dollars",
    limits = c(la_lo, la_hi),
    breaks = seq(1.6, 2.2, 0.1),
    labels = number_format(accuracy = 0.1),
    sec.axis = sec_axis(
      transform = unscale_left_b,
      name   = "Log(p90)\u2013log(p50)",
      breaks = seq(0.5, 1.1, 0.1),
      labels = number_format(accuracy = 0.1)
    )
  ) +
  scale_x_continuous(
    breaks = c(1974, 1980, 1985, 1990, 1995, 2000, 2005, 2010, 2015, 2020, 2024),
    limits = c(1974, 2025)
  ) +
  scale_color_manual(
    name = NULL,
    values = c(
      "Avg. real value of state/fed. mins (L axis)" = "#1F3E6E",
      "Real value of fed. min. (L axis)"            = "#8B1A1A",
      "log(p90)-log(p50), female (R axis)"          = "#228B22",
      "log(p90)-log(p50), male (R axis)"            = "#D46A00"
    )
  ) +
  scale_linetype_manual(
    name = NULL,
    values = c(
      "Avg. real value of state/fed. mins (L axis)" = "dashed",
      "Real value of fed. min. (L axis)"            = "dotted",
      "log(p90)-log(p50), female (R axis)"          = "solid",
      "log(p90)-log(p50), male (R axis)"            = "solid"
    )
  ) +
  guides(
    color    = guide_legend(nrow = 2),
    linetype = guide_legend(nrow = 2)
  ) +
  labs(x = NULL) +
  stata_theme +
  theme(
    legend.position    = "bottom",
    legend.margin      = margin(0, 0, 0, 0),
    axis.title.y       = element_text(size = 7),
    axis.title.y.right = element_text(size = 7)
  )


# =============================================================================
# FIGURE 7 HELPER — used for all four sub-periods
# =============================================================================

make_fig7 <- function(df, period_label, ylims = c(-0.3, 0.7), ybreaks = seq(-0.3, 0.7, 0.1)) {
  ggplot(df, aes(x = p)) +
    geom_line(aes(y = b4_marg,  color = "Marginal effect"), linetype = "solid",  linewidth = 1.1) +
    geom_line(aes(y = ub4_marg, color = "95% CI bounds"),  linetype = "dashed", linewidth = 1.1) +
    geom_line(aes(y = lb4_marg, color = "95% CI bounds"),  linetype = "dashed", linewidth = 1.1) +
    geom_hline(yintercept = 0, linewidth = 0.4, color = "black") +
    scale_x_continuous(
      name   = "Percentile",
      breaks = seq(0, 100, 10),
      limits = c(5, 95)
    ) +
    scale_y_continuous(
      name   = "",
      limits = ylims,
      breaks = ybreaks,
      labels = number_format(accuracy = 0.1)
    ) +
    scale_color_manual(
      values = c("Marginal effect" = "#0000CD", "95% CI bounds" = "#8B1A1A")
    ) +
    labs(subtitle = period_label) +
    stata_theme +
    theme(
      legend.position = "none",
      plot.subtitle   = element_text(size = 8, hjust = 0.5)
    )
}

fig7_1979_1989_plot <- make_fig7(
  fig7_1979_1989, "1979\u20131989",
  ylims   = c(-25, 28),
  ybreaks = c(-25, -15, -5, 0, 5, 15, 25)
)

fig7_1979_1991_plot <- make_fig7(fig7_1979_1991, "1979\u20131991")
fig7_1979_2012_plot <- make_fig7(fig7_1979_2012, "1979\u20132012")
fig7_1979_2024_plot <- make_fig7(fig7_1979_2024, "1979\u20132024")


# =============================================================================
# FIGURE 10 HELPER — used for fig10a, fig10b, fig10c
# =============================================================================

make_fig10 <- function(df, show_legend = FALSE) {
  p <- ggplot(df, aes(x = year)) +
    geom_line(aes(y = me_lvl,  color = "Estimated marginal effect"),
              linetype = "dashed", linewidth = 1.0) +
    geom_line(aes(y = spiketl, color = "Density bounds"),
              linetype = "solid",  linewidth = 1.0) +
    geom_line(aes(y = spiketu, color = "Density bounds"),
              linetype = "solid",  linewidth = 1.0) +
    geom_hline(yintercept = 0, linewidth = 0.5, color = "black") +
    scale_x_continuous(
      breaks = c(1979, 1985, 1990, 1995, 2000, 2005, 2010, 2015, 2020, 2024),
      limits = c(1979, 2025)
    ) +
    scale_y_continuous(
      name   = "Effect of minimum wage on mean",
      limits = c(-0.1, 0.2),
      breaks = seq(-0.1, 0.2, 0.05),
      labels = number_format(accuracy = 0.01)
    ) +
    scale_color_manual(
      name = NULL,
      values = c(
        "Estimated marginal effect" = "#8B1A1A",
        "Density bounds"            = "black"
      )
    ) +
    labs(x = NULL) +
    stata_theme

  if (show_legend) {
    p <- p +
      guides(color = guide_legend(
        override.aes = list(linetype = c("dashed", "solid")),
        nrow = 2
      )) +
      theme(legend.position = "bottom")
  } else {
    p <- p + theme(legend.position = "none")
  }
  p
}

fig10a_plot <- make_fig10(fig10a, show_legend = FALSE)
fig10b_plot <- make_fig10(fig10b, show_legend = FALSE)
fig10c_plot <- make_fig10(fig10c, show_legend = TRUE)

```

## Section I

### Introduction

Income Inequality is an inevitability of any urban, modern labor market. Since the 1970's, large divergences in income inequality have drawn sustained attention from economists, policymakers, and the public alike. A central question in this literature concerns what drives the gap between lower-wage and median-wage workers; that is, lower-tail inequality. One of the most prominent contested explanations is the erosion of the real minimum wage.

The federal minimum wage has remain at \$7.25 per hour since 2009. In real terms, its value has declined substantially relative to the wages of median workers in the decade that followed, and has seen a more drastic decline in the years that followed. However, the policy landscape at the state level has changed considerably: as of the mid 2020's, the majority of states have enacted minimum wages that exceed the federal floor, and the average effective minimum wage across states has risen meaningfully since 2012. This divergence between the stagnant federal minimum and rising state minimums creates empirical variation that prior studies, whose data ends in 2012, could not exploit.

The study that lays the foundation in this literature, @lee1999wage, argued that declines in the real minimum wage explained the vast majority (roughly 80%) of the rise in lower-tail wage inequality during the 1980's. This impact is particularly pronounced among women. This conclusion was influential but has not gone unchallenged. @autor2016minimum demonstrated that Lee's estimates suffered from a systematic upward bias: because the minimum wage and the median wage both enter the OLS specification, measurement error in the median wage generated a mechanical positive correlation that overstates the minimum wage's reach. After correcting for this bias via an instrument variables approach, the authors find that the minimum wage explains a more modest amount (30-40%) of lower-tail female wage inequality, with negligible effects for men. Their findings suggest the minimum wage's influen ce is largely confined to workers at or very near the wage floor, with apparent spillovers to higher percentiles driven primarily by measurement error rather than true policy effects.

This paper extends that reanalysis to the present (or as close to the present as current data would allow). The question motivating this extension is whether the constinued growth in state minimum wages since 2012, and the additional twelve years of wage data now available, alter these conclusions. From analyzing Figure 1, we see that the real federal minimum wage has plumeted; the real average minimum wage has not. Yet, in spite of the real average minimum wage increasing, income inequality across the board has been highlighted as increasing over the years. This disconnect gives reason to expect the estimated effect might diminish further than what @autor2016minimum estimated. If state minimum wages have increased broadly, the binding minimum wage is now closer to the median in many states, compressing the distribution at the bottom. Under the framework presented in @autor2016minimum (that being, where the minimum wage's effect is measured relative to the median) a higher binding minimum reduces the identifying variation and may produce smaller estimated effects. Additionally, if true spillovers are minimal, additional data from a period of rising minimum wages should continue to support the measurement error interpretation.

The remainder of this paper proceeds as follows. Section II will further review the relevant literature, tracing the debate from @lee1999wage through @autor2016minimum and situating this extension within that scholarly conversation. Section III describes the data sources and sample construction. Section IV details the identification strategy, including the instrument variables approach used to correct for measurement error bias. Section V presents results, including replication of the original figures and regression tables alongside their updated counterparts. Section VI concludes with an overview of this study as well as a discussion of limitations and directions for future research.

## Section II

### Literature Review

This paper sits within a literature examining the relationship between the minimum wage and lower-tail wage inequality in the United States.

The initial study (@lee1999wage) poses that essentially all income inequality (roughly 80%), especially at the lower tail, can be primarily explained by decreases in the real minimum wage. For clarity, the real minimum wage can be explained as the real value of the minimum wage. Over time, if there are no increases to the value of the minimum wage, inflation will effectively make the minimum wage less effective. This varies primarily across gender lines, where for women it explains much more inequality than it does in men.

The subsequent study, which is the one being extended (@autor2016minimum), finds that much less, around 30% of lower tail income inequality can be explained by the minimum wage. This paper hypothesizes that the minimum wage's contribution to lower-tail inequality will be smaller still once data through 2024 are incorporated.

A crucial dimension of both @lee1999wage and @autor2016minimum is the role of gender in driving these distributional effects. Due to there being a higher density of female workers historically clustered near the income floor, the minimum wage "bite" is significantly larger for women than men. Consequently, both studies find that changes in the real value of the minimum wage have a much more pronounced impact on female wage inequality. While @lee1999wage attributed nearly the entirety of the rise in female lower-tail inequality during the 1980s to the erosion of the minimum wage, @autor2016minimum show that after correcting for measurement error, the policy explains a more modest 30% to 40% of the growth in the female 50/10 wage gap, and has a negligible effect on male workers.

The Figures and Tables portion of this study will show some of the remaining images that are not discussed in depth here. The authors use these figures in the initial work to express causes and reasons to conduct their study in the way that they do. As I am merely extending their work, I feel that I do not need to reiterate their motivations. I do, however, extend their figures with the new data gathered.

## Section III

### Data

The study being extended provides and uses data from 1973-2012. The data comes from CPS monthly outgoing rotation group (morg) data, which is provided by the UNICON corporation. For this extension, further data from the same source will be compiled and cleaned to present an additional 10 years worth of findings. @autor2016minimum determine an extension that could give more conclusive answers would require better wage data. The cleaner that is used in this study, as well as @autor2016minimum, comes from earlier projects from similar authors: @autor2008.

In 2019, the National Bureau of Economic Research began compiling the CPS morg data into easy to access .dta files, from 1979 to 2024. The last update to this series of data was 05/20/2025 for the 2024 data set. As @autor2016minimum provides this data up until 2012, the remaining data up until the present will come from this source (@NBER_MORG). Data for CPI is annual CPI sourced from the Bureau of Labor Statistics (@BLSData2026). This data, like the CPI data given by the original authors are based at 1982-84=100. As for state minimum wage data, data set gathered comes from the Department of Labor (@USDOLMinimumWageHistory). All data being added covers the years 2012 to 2024.

The data will be formatted to show figures and tables for males, females, and pooled males and females.

## Section IV

### Identification Strategy

@lee1999wage presents the following OLS model, which is also used in @autor2016minimum:

$$
w_{st}(p)-w_{st}(50)=\beta_1(p)[w^m_{st}-w_{st}(50)]+\beta_2(p)[w^m_{st}-w_{st}(50)]^2
$$ {#eq-numberone} $$
+\sigma_{s0}(p)+\sigma_{s1}(p)*time_t+\gamma^\sigma_t(p)+\epsilon^\sigma_{st}(p)
$$  

For this equation, $w_{st}(p)$ represents the log real wage, $\sigma_{s0}(p)$ time-invariant state effects, $\sigma_{s1}(p)$ state-specific trends, $\gamma^\sigma_t(p)$ time effects, and $\epsilon^\sigma_{st}(p)$ transitory effects; at percentile $p$ in state $s$ at time $t$. From @lee1999wage, the bindingness of the minimum wage is defined to be the log difference between the minimum wage and the median. By bindingness of the minimum wage, they mean the minimum wages proximity to the median wage. This will result in a less negative value, or a greater effective minimum wage. This is also referred to as a "bite". The model is identified using three distinct scenarios characterizing how the wage distribution responds to a change in the minimum wage.

Scenario 1: no spillovers, no disemployment. This means that when there is a change in the minimum wage, those that were making the minimum wage before the change will have their wages bumped up and there will be no other changes. There is no change in employment and no change in the wages of other around the minimum wage.

Scenario 2: spillovers, no disemployment. This means that when there is a change in the minimum wage, those that were making the minimum wage before the change will have their wages bumped up. Those who were in supervisory or other hierarchical roles above those earning minimum wage would have their wage bumped up to some value that would maintain the hierarchy. For example, if the minimum wage were \$7.25 and a worker earning that wage had a supervisor making \$15 an hour; a change in the minimum wage to \$15 would cause the minimum wage worker and their supervisor to see a bump in pay so as to maintain the hierarchy of the working conditions.

Scenario 3: no spillovers, full disemployment. This means that when there is a change in the minimum wage, those that were making the minimum wage before the change will become unemployed or replaced with automation, etc. Those who were in supervisory roles would not see increases in their pay.

A combination of Scenario 2 and 3 is used, but due to measurement error, there are inaccurate estimations dragging variables together. This is overcome via an instrument variable explained later (methodology deriving from @durbin1954errors). In survey data, individuals frequently misreport or round their earnings. This introduces random noise into the observed wage distribution. As there are benchmarks for every percentile against the observed median wage in the OLS model, any sampling error in the median affects both the dependent variable and the independent variable simultaneously.

@autor2016minimum model this measurement error with the following equations:

$$
w(p^*) \equiv max[w^m,w^*(p)],
$$ {#eq-numbertwo}

$$
w_i=w(p*)+\epsilon_i
$$ {#eq-numberthree}

 

When the median is over-measured in a given state-year cell ($\epsilon_{st}>0$), the dependent variable ($w^p_{st}-w_{st}(50)$) artificially decreases. At the same time, the independent variable \[$w^m_{st}-e_{st}(50)$\] also decreases, becoming more negative. Conversely, when the median is under represented or measured ($\epsilon_{st}<0$), both terms artificially increase. This common error term forces the two variables to move in tandem, generating a mechanical, upward biased positive correlation. The resulting bias mimics the statistical signature of a spillover effect. As a result, OLS models mistakenly interpret the measurement noise as a real economic ripple that pulls up the wages for high earning workers. By overstating the reach of the minimum wage, the OLS framework incorrectly attributes a reduction in inequality to the minimum wage when it is actually just the compression of measurement error.

Once this measurement error is purged through the instrument variable, the percieved spillovers at higher percentiles disappear. Thus implying that the true range of the minimum wage is much more modest, extending only to the bottom percentiles of the distribution.

@autor2016minimum expresses possible cause of bias in the estimates with the following equation:

$$
w_{st}(50)=\mu_{s0}+\mu_{s1}*time_t+\gamma^\mu_t+\epsilon^\mu_{st}
$$ {#eq-numberfour}

 

For this equation, $w_{st}(50)$ retains its interpretation from the previous equation. That is, it represents the median wage (wage at the $p^{th}$ percentile, so the 50th percentile) for a given state at a given time. Furthermore, $\mu_{s0}$ represents the state effect, $\mu_{s1}$ the state trend, $\gamma^\mu_t$ the common year effect, and $\epsilon^\mu_{st}$ the transitory effect.

The authors then go on to take an instrument variables (IV) approach for the model. To do this, they instrument the minimum wage; For 2SLS, the effective minimum ($[w_{st}^m-w_{st}(50)]$) and its square ($[w^m_{st}-w_{st}(50)]^2$) are instrumented by the log of the minimum wage, the square of the log of the minimum wage, and the logged minimum wage interacted with the average real log median wage ($lmin*avg\_median$). These data points are anchored with annual CPI.

To replicate previous work, all that needed to be done was to lightly edit data provided by the authors. To extend the work, new data and information is gathered and all that needs to be done is to simply extend with the new data and additional years. The CPS morg data provided by the NBER resembles the raw data that was cleaned by @autor2016minimum. In order to have the data appropriately reflect the format, a cleaner is used. This cleaner is similar to one used in @autor2008, and it is the basis for the initial study. The authors clean the raw data and work with the output. The data for CPI and state minimum wages require no cleaning; as mentioned above, CPI is already formatted the same between the new and old data. The state minimum wage data is not very debatable, and thereby requires no reworking.

One replication issue warrants disclosure. In the truespike portion of the analysis, the maximum internal matrix dimension (which governs the number of variables that can be included) required lowering from a matsize of 1000 to 800. All output ran successfully under this constraint, and I do not believe it affected the results, but the deviation from the original specification is noted here for transparency.

## Section V

### Results

The initial study presents that there has been little lower tail wage inequality changes since the 1980's. This is seen in Figure 1A.

```{r,message=FALSE,echo=FALSE,warning=FALSE}
fig1a_plot
```

Comparing the updated regression tables to the initial results reveals a consisten pattern: the estimated effect of the minimum wage on lower-tail inequality is somewhat smaller in the extended sample. The new estimates at the tail end of earners (roughly 20-30%) are slightly lower than the estimates for their counterparts in the initial study (roughly 30-40%). There is, however, heavier statistical significance throughout the Levels 2SLS model in the updated results, suggesting the relationships that do survive are more precisely estimated.

One notable anomaly in the update female results under the 2SLS Levels model is that the estimates for p(10) and p(20) are both larger than the estimate for p(5), which runs counter to the expected monotonic pattern. This could warrant attention in future work, but it could also mean that the minimum wage has a greater impact on slightly higher than the bottom earning percentiles.

Figure 7 plots the estimates of marginal effects of the minimum wage on certain percentiles across the pooled distribution over four time periods. The initial study accounted for the first three and the extension provides the fourth. The extension adds 12 years of data on top of the 21 additional years already incorporated by @autor2016minimum relative to @lee1999wage, and Figure 7 illustrates that this additional variation meaningfully shifts the estimated marginal effects at the lower tail.

Figure 7A (1979-1989):

```{r,echo=FALSE,message=FALSE,warning=FALSE}
fig7_1979_1989_plot
```

Figure 7B (1979-1991):

```{r,echo=FALSE,message=FALSE,warning=FALSE}
fig7_1979_1991_plot
```

Figure 7C: (1979-2012):

```{r,echo=FALSE,warning=FALSE,message=FALSE}
fig7_1979_2012_plot
```

Figure 7D (1979-2024):

```{r,echo=FALSE,warning=FALSE,message=FALSE}
fig7_1979_2024_plot
```

The truespike analysis tests whether the observed concentration of wages near the minimum reflects a true policy effect or is an artifact of the wage distribution that would exist absent the legislation. To isolate the true policy induced spike, a counterfactual wage distribution is modeled. By using variation across states (as well as the difference between the federal and state minimum wage), the initial study determines how wages would look absent the minimum wage. Under an alternative hypothesis that the true spillovers are present, the marginal effect on the mean should exceed the true spike. Figure 10, in its extended form, shows that while the mean lies outside the bounds in some years, the evidence is insufficient to reject the null hypothesis that apparent spillovers above the minimum wage floor reflect measurement error rather than genuine policy effects.

Figure 10A:

```{r,echo=FALSE,warning=FALSE,message=FALSE}
fig10a_plot
```

Figure 10B:

```{r,echo=FALSE,message=FALSE,warning=FALSE}
fig10b_plot
```

Figure 10C:

```{r,echo=FALSE,warning=FALSE,message=FALSE}
fig10c_plot
```

Table 2:
```{r,echo=FALSE,message=FALSE,warning=FALSE, results='asis'}
# =============================================================================
# Table 2 — Initial and Updated
# Panels A (Female), B (Male), C (Pooled) in one longtable per dataset.
# longtable allows page breaks mid-table so nothing gets cut off.
# [H] not used with longtable — longtable is not a float, it flows inline.
#
# YAML requirements:
#   format:
#     pdf:
#       include-in-header:
#         text: |
#           \usepackage{longtable}
#           \usepackage{booktabs}
# =============================================================================

library(haven)
library(dplyr)
library(knitr)
library(kableExtra)

# ── Shared formatter ──────────────────────────────────────────────────────────
fmt_cell <- function(b, se) {
  if (is.na(b) || is.na(se)) return("")
  z     <- abs(b / se)
  stars <- dplyr::case_when(
    z > qnorm(0.995) ~ "***",
    z > qnorm(0.975) ~ "**",
    z > qnorm(0.95)  ~ "*",
    TRUE             ~ ""
  )
  coef_str <- formatC(round(b, 2), format = "f", digits = 2)
  se_str   <- formatC(round(se, 2), format = "f", digits = 2)
  kableExtra::linebreak(paste0(coef_str, stars, "\n(", se_str, ")"), align = "c")
}

# ── Shared constants ──────────────────────────────────────────────────────────
pctiles    <- c(5, 10, 20, 30, 40, 75, 90, 100)
row_labels <- c("p(5)", "p(10)", "p(20)", "p(30)", "p(40)",
                "p(75)", "p(90)", "Var. of log wage")

bottom_rows <- data.frame(
  V1 = c("Levels/first-differenced", "Year FE", "State FE", "State trends"),
  V2 = c("Levels", "Yes", "Yes", "Yes"),
  V3 = c("FD",     "Yes", "Yes", "No"),
  V4 = c("Levels", "Yes", "Yes", "Yes"),
  V5 = c("FD",     "Yes", "Yes", "No"),
  V6 = c("Levels", "Yes", "No",  "No"),
  stringsAsFactors = FALSE
)

col_names <- kableExtra::linebreak(
  c("", "OLS\n(1)", "OLS\n(2)", "2SLS\n(3)", "2SLS\n(4)", "OLS\nLee Spec.\n(5)"),
  align = "c"
)

# ── Panel builder ─────────────────────────────────────────────────────────────
build_panel <- function(df, suffix) {
  bvars <- paste0(c("b3_marg", "b7_marg", "b4_marg", "b8_marg", "b1_marg"), suffix)
  rows  <- lapply(seq_along(pctiles), function(i) {
    b_row  <- df |> filter(p == pctiles[i], est == "b")
    se_row <- df |> filter(p == pctiles[i], est == "se")
    cells  <- sapply(bvars, function(v)
      fmt_cell(as.numeric(b_row[[v]]), as.numeric(se_row[[v]])))
    c(row_labels[i], cells)
  })
  do.call(rbind, rows) |> as.data.frame(stringsAsFactors = FALSE)
}

# ── Full table builder ────────────────────────────────────────────────────────
render_table2 <- function(file_path, caption_text) {
  df <- read_dta(file_path)

  panel_f   <- build_panel(df, "_f")
  panel_m   <- build_panel(df, "_m")
  panel_all <- build_panel(df, "_all")

  vnames <- paste0("V", 1:6)
  names(panel_f) <- names(panel_m) <- names(panel_all) <- vnames

  hdr_f   <- setNames(as.data.frame(matrix(c("Panel A. Females", rep("", 5)), nrow = 1),
                                    stringsAsFactors = FALSE), vnames)
  hdr_m   <- setNames(as.data.frame(matrix(c("Panel B. Males",   rep("", 5)), nrow = 1),
                                    stringsAsFactors = FALSE), vnames)
  hdr_all <- setNames(as.data.frame(matrix(c("Panel C. Pooled",  rep("", 5)), nrow = 1),
                                    stringsAsFactors = FALSE), vnames)
  names(bottom_rows) <- vnames

  full_table <- bind_rows(hdr_f, panel_f, hdr_m, panel_m, hdr_all, panel_all, bottom_rows)

  kbl(
    full_table,
    col.names = col_names,
    align     = c("l", rep("c", 5)),
    booktabs  = TRUE,
    escape    = FALSE,
    format    = "latex",
    longtable = TRUE,          # allows page breaks — no float, no cutoff
    linesep   = "",
    caption   = caption_text
  ) |>
    kable_styling(
      latex_options = c("repeat_header"),   # reprint header on each continued page
      font_size     = 10,
      full_width    = FALSE
    ) |>
    row_spec(c(1, 10, 19), bold = TRUE) |>
    add_header_above(
      c(" " = 1, "OLS" = 2, "2SLS" = 2, "OLS Lee Spec." = 1),
      bold = TRUE
    )
}

# ── Render both tables ────────────────────────────────────────────────────────
render_table2("table-2.dta",         "TABLE 2---OLS and 2SLS Relationship (Initial)")

cat("\n\\bigskip\n")   # visual gap between the two tables

render_table2("table-2_updated.dta", "TABLE 2---OLS and 2SLS Relationship (Updated, 1979--2024)")


```


## Section VI

### Conclusion

This paper finds evidence that the minimum wage's contribution to lower-tail wage inequality is smaller in the extended sample than reported in either @lee1999wage or @autor2016minimum, reinforcing the direction of revision that the later work introduced. While the minimum wage does have a measurable impact on income inequality, the impact is not nearly as large as was reported in the 1990's.

Analyzing the minimum wage inherently argues that there is no possible lower wage alternative. The entire study and argument will remain outside the bounds of reality where corruption or illegal activities occur. In spite of strong American institutional presence, to say these factors do not impact the American economy would be illegitimate and insincere. For future studies, I would like to find a way to expand the data to appropriately include illegal impacts on wages. This would obviously impact some states more than others and would require an entirely new series of data as CPS is self reported labor data. Additionally, the updated data does not include the market volatility and shocks of the current presidential administration. Outside of immigration shocks; tariff activity, inflationary pressures, and oil shocks are likely to have some impact on results, though year fixed effects should absorb much of this variation.

Future research on this topic would benefit from reforming the model itself rather than simply extending the data. Immigration shocks, given their likely concentration at the lower tail of the wage distribution, represent a particularly promising avenue. Other factors, such as union presence, unemployment, shifting shares of production between capital and labor all impact wages and by extension income inequality. While it can be difficult to model such large causal interpretations, it is important to note its impact on actual circumstances.

\newpage

## Figures and Tables

```{r,echo=FALSE,message=FALSE,warning=FALSE}
# =============================================================================
# R Code to Reproduce Stata .gph Figures — Batch 2
# Figures: fig2, fig3 (all/m/f), fig4 (all/m/f × lvl/fd), fig5 (all/m/f)
# Generated from parsed Stata serset binary data
# =============================================================================

library(ggplot2)
library(scales)

# ── Shared theme (mimics Stata's stcolor scheme) ─────────────────────────────
stata_theme <- theme_bw() +
  theme(
    panel.background   = element_rect(fill = "white", color = "white"),
    plot.background    = element_rect(fill = "white", color = "white"),
    panel.border       = element_rect(color = "grey80"),
    panel.grid.major   = element_line(color = "white", linewidth = 0.4),
    panel.grid.minor   = element_blank(),
    legend.background  = element_rect(fill = "white", color = NA),
    legend.key         = element_rect(fill = "white"),
    legend.position    = "bottom",
    legend.text        = element_text(size = 7),
    axis.text          = element_text(size = 7),
    axis.title         = element_text(size = 7),
    plot.margin        = margin(4, 6, 4, 6, "pt")
  )

# =============================================================================
# DATA
# =============================================================================

# ── fig2 ─────────────────────────────────────────────────────────────────────
# Share of workers at or below the minimum wage (1979–2024)
# sharef = female, sharem = male, shareall = pooled
# Note: sharef for 2024 was not stored in the serset (truncated); set to NA.
fig2 <- data.frame(
  year     = 1979:2024,
  sharef   = c(0.132378, 0.130807, 0.106315, 0.098128, 0.089145, 0.079971, 0.071709, 0.063531, 0.059300, 0.053701, 0.053833, 0.069676, 0.065143, 0.057710, 0.057905, 0.051801, 0.049058, 0.063536, 0.064780, 0.053585, 0.048408, 0.045362, 0.042920, 0.039790, 0.039223, 0.041631, 0.040835, 0.053000, 0.055897, 0.061862, 0.061596, 0.059499, 0.076108, 0.070850, 0.071871, 0.076798, 0.076460, 0.073503, 0.074848, 0.085930, 0.066648, 0.067043, 0.061388, 0.068327, 0.067115, NA),
  sharem   = c(0.046650, 0.055494, 0.055695, 0.049577, 0.048330, 0.041194, 0.037272, 0.033361, 0.030559, 0.028919, 0.027694, 0.028192, 0.037848, 0.036209, 0.034414, 0.031479, 0.027938, 0.028493, 0.037542, 0.039003, 0.030774, 0.028151, 0.027967, 0.027975, 0.025877, 0.025116, 0.024948, 0.024920, 0.032532, 0.035686, 0.042107, 0.042768, 0.039677, 0.051417, 0.047412, 0.054413, 0.051434, 0.054882, 0.050723, 0.052169, 0.057473, 0.043124, 0.047646, 0.044289, 0.048840, 0.048790),
  shareall = c(0.077955, 0.086096, 0.085906, 0.072807, 0.068906, 0.060939, 0.055009, 0.049487, 0.044504, 0.041834, 0.038791, 0.039154, 0.051562, 0.048776, 0.044558, 0.042894, 0.038237, 0.037400, 0.048868, 0.050225, 0.040785, 0.037048, 0.035633, 0.034573, 0.032058, 0.031349, 0.032308, 0.031942, 0.041581, 0.044719, 0.051088, 0.051294, 0.048569, 0.062483, 0.057935, 0.062343, 0.062809, 0.064549, 0.060935, 0.062361, 0.070338, 0.053748, 0.056482, 0.052031, 0.057658, 0.057130)
)

# ── fig3 ─────────────────────────────────────────────────────────────────────
# Marginal effects by wage percentile — OLS levels (b3), 1979–2024
fig3_all <- data.frame(
  p            = 5:95,
  b3_all_marg  = c(0.297064, 0.282529, 0.266107, 0.248708, 0.249791, 0.232458, 0.207572, 0.189672, 0.185329, 0.163781, 0.152559, 0.147977, 0.142167, 0.147533, 0.139095, 0.129224, 0.116372, 0.101167, 0.085884, 0.090870, 0.089161, 0.073757, 0.065149, 0.072292, 0.065688, 0.067111, 0.060084, 0.058191, 0.050635, 0.050220, 0.043320, 0.039280, 0.038992, 0.034673, 0.039754, 0.037849, 0.030222, 0.033499, 0.032955, 0.028092, 0.022136, 0.026711, 0.021504, 0.016932, 0.012612, 0.000000, 0.005357, 0.020064, 0.017949, 0.028672, 0.024626, 0.024274, 0.024275, 0.026137, 0.027050, 0.024145, 0.022380, 0.022832, 0.021188, 0.013930, 0.022339, 0.028505, 0.027698, 0.032287, 0.032946, 0.034840, 0.035810, 0.037741, 0.034770, 0.043648, 0.038386, 0.043306, 0.047007, 0.044856, 0.048458, 0.052347, 0.051116, 0.054583, 0.051864, 0.056123, 0.058663, 0.062336, 0.069465, 0.053630, 0.057088, 0.064409, 0.076408, 0.088540, 0.086601, 0.089275, 0.095441),
  ub3_all_marg = c(0.336826, 0.320570, 0.301028, 0.284735, 0.286677, 0.274846, 0.247498, 0.227601, 0.222976, 0.198506, 0.187281, 0.185200, 0.180750, 0.186140, 0.185004, 0.175370, 0.155218, 0.137099, 0.117826, 0.125494, 0.123573, 0.104937, 0.099032, 0.106756, 0.094634, 0.089264, 0.084668, 0.083353, 0.071629, 0.069960, 0.059115, 0.055133, 0.055596, 0.049640, 0.063564, 0.058922, 0.048685, 0.046344, 0.052168, 0.045195, 0.037188, 0.043571, 0.034657, 0.025271, 0.022520, 0.000000, 0.010162, 0.027441, 0.024851, 0.039641, 0.037329, 0.033912, 0.035994, 0.035565, 0.039462, 0.037662, 0.034198, 0.033555, 0.035958, 0.028037, 0.039563, 0.046402, 0.047331, 0.050278, 0.053693, 0.055008, 0.057574, 0.062426, 0.056512, 0.066621, 0.059846, 0.067232, 0.069483, 0.070078, 0.072336, 0.079162, 0.078909, 0.081715, 0.076381, 0.085614, 0.085407, 0.094345, 0.105807, 0.089878, 0.098721, 0.110345, 0.130600, 0.138281, 0.132154, 0.145337, 0.156385),
  lb3_all_marg = c(0.257302, 0.244488, 0.231186, 0.212680, 0.212905, 0.190071, 0.167645, 0.151742, 0.147683, 0.129057, 0.117836, 0.110754, 0.103585, 0.108926, 0.093186, 0.083079, 0.077527, 0.065235, 0.053941, 0.056245, 0.054750, 0.042577, 0.031266, 0.037827, 0.036741, 0.044958, 0.035499, 0.033030, 0.029642, 0.030479, 0.027525, 0.023428, 0.022389, 0.019706, 0.015943, 0.016776, 0.011759, 0.020654, 0.013741, 0.010989, 0.007084, 0.009852, 0.008351, 0.008593, 0.002704, 0.000000, 0.000551, 0.012687, 0.011047, 0.017702, 0.011923, 0.014636, 0.012556, 0.016708, 0.014638, 0.010629, 0.010561, 0.012109, 0.006419, -0.000177, 0.005116, 0.010609, 0.008065, 0.014296, 0.012198, 0.014673, 0.014047, 0.013055, 0.013028, 0.020674, 0.016927, 0.019380, 0.024532, 0.019634, 0.024580, 0.025532, 0.023322, 0.027450, 0.027347, 0.026632, 0.031919, 0.030328, 0.033123, 0.017381, 0.015455, 0.018473, 0.022215, 0.038800, 0.041049, 0.033213, 0.034498)
)

fig3_f <- data.frame(
  p           = 5:95,
  b3_f_marg   = c(0.346880, 0.349504, 0.345746, 0.322709, 0.299059, 0.290430, 0.281881, 0.263362, 0.244216, 0.226208, 0.214312, 0.190090, 0.177684, 0.176537, 0.172033, 0.168200, 0.157311, 0.154242, 0.144935, 0.129926, 0.119713, 0.110364, 0.099881, 0.095955, 0.085325, 0.086120, 0.075646, 0.070390, 0.062894, 0.061866, 0.056808, 0.055721, 0.055831, 0.050048, 0.050168, 0.047400, 0.048506, 0.053905, 0.050345, 0.039622, 0.038596, 0.038648, 0.037633, 0.024290, 0.014065, 0.000000, 0.006271, 0.012441, 0.019364, 0.026607, 0.026549, 0.031935, 0.036885, 0.041038, 0.040252, 0.040185, 0.036253, 0.045647, 0.042806, 0.040156, 0.045770, 0.051531, 0.052352, 0.048170, 0.057360, 0.055360, 0.054740, 0.051025, 0.053302, 0.051647, 0.063763, 0.064378, 0.059223, 0.068389, 0.064006, 0.062141, 0.059465, 0.067814, 0.066542, 0.074127, 0.076481, 0.076812, 0.076420, 0.078055, 0.077309, 0.076520, 0.082113, 0.073024, 0.082105, 0.094336, 0.089588),
  ub3_f_marg  = c(0.392917, 0.386697, 0.379835, 0.356677, 0.329938, 0.320225, 0.316117, 0.293964, 0.276374, 0.256908, 0.242501, 0.224039, 0.208300, 0.207133, 0.202867, 0.199727, 0.186832, 0.183804, 0.176603, 0.159450, 0.151926, 0.140044, 0.124829, 0.116546, 0.108769, 0.117132, 0.104752, 0.094683, 0.087485, 0.080408, 0.077471, 0.073199, 0.072207, 0.070603, 0.068266, 0.067397, 0.064756, 0.067963, 0.064346, 0.056204, 0.052326, 0.050828, 0.048144, 0.032929, 0.020983, 0.000000, 0.015495, 0.023188, 0.028541, 0.039633, 0.035695, 0.046577, 0.053812, 0.054385, 0.054434, 0.056793, 0.052730, 0.061768, 0.058559, 0.055803, 0.061194, 0.071477, 0.066563, 0.066509, 0.075448, 0.072834, 0.074593, 0.070777, 0.074330, 0.077564, 0.086339, 0.088955, 0.086594, 0.095923, 0.092240, 0.091234, 0.090303, 0.097835, 0.098512, 0.108830, 0.108325, 0.110245, 0.107787, 0.107734, 0.108157, 0.108520, 0.110163, 0.103364, 0.121228, 0.134043, 0.131196),
  lb3_f_marg  = c(0.300843, 0.312311, 0.311657, 0.288740, 0.268181, 0.260636, 0.247645, 0.232760, 0.212058, 0.195508, 0.186123, 0.156140, 0.147068, 0.145940, 0.141199, 0.136672, 0.127789, 0.124679, 0.113266, 0.100403, 0.087500, 0.080683, 0.074934, 0.075363, 0.061882, 0.055109, 0.046541, 0.046097, 0.038303, 0.043324, 0.036146, 0.038244, 0.039455, 0.029492, 0.032071, 0.027402, 0.032256, 0.039846, 0.036344, 0.023040, 0.024867, 0.026468, 0.027122, 0.015651, 0.007146, 0.000000, -0.002954, 0.001693, 0.010186, 0.013580, 0.017403, 0.017294, 0.019958, 0.027692, 0.026070, 0.023577, 0.019775, 0.029525, 0.027053, 0.024508, 0.030347, 0.031584, 0.038142, 0.029831, 0.039271, 0.037886, 0.034888, 0.031273, 0.032273, 0.025731, 0.041187, 0.039800, 0.031852, 0.040856, 0.035772, 0.033047, 0.028627, 0.037793, 0.034572, 0.039424, 0.044637, 0.043379, 0.045052, 0.048375, 0.046461, 0.044521, 0.054063, 0.042684, 0.042983, 0.054629, 0.047981)
)

fig3_m <- data.frame(
  p           = 5:95,
  b3_m_marg   = c(0.258169, 0.228842, 0.229533, 0.213809, 0.208887, 0.182953, 0.164278, 0.163331, 0.152910, 0.148299, 0.123351, 0.129851, 0.127014, 0.132500, 0.114881, 0.104996, 0.094653, 0.086087, 0.084598, 0.081777, 0.075629, 0.078936, 0.070701, 0.063918, 0.064014, 0.060785, 0.050781, 0.048574, 0.036017, 0.033592, 0.031452, 0.034171, 0.034386, 0.035434, 0.033963, 0.037701, 0.041953, 0.030243, 0.022283, 0.021857, 0.019295, 0.018652, 0.020978, 0.012667, 0.008853, 0.000000, 0.012218, 0.022536, 0.022444, 0.023673, 0.018587, 0.011211, 0.012383, 0.016862, 0.017740, 0.026338, 0.023588, 0.023657, 0.027385, 0.033019, 0.031519, 0.031598, 0.033927, 0.033844, 0.034485, 0.035070, 0.040458, 0.044770, 0.043730, 0.054401, 0.051361, 0.054272, 0.055473, 0.048646, 0.057317, 0.060575, 0.064706, 0.069993, 0.068081, 0.073508, 0.068255, 0.076965, 0.080073, 0.085512, 0.086491, 0.096639, 0.100039, 0.100222, 0.105586, 0.109491, 0.105995),
  ub3_m_marg  = c(0.312151, 0.273967, 0.282839, 0.257392, 0.249631, 0.218802, 0.202200, 0.199993, 0.195183, 0.189861, 0.164931, 0.169011, 0.166105, 0.171281, 0.149613, 0.133103, 0.123317, 0.115573, 0.115139, 0.112923, 0.109454, 0.109104, 0.096766, 0.085346, 0.084510, 0.082950, 0.068962, 0.065778, 0.052298, 0.050570, 0.048420, 0.051955, 0.047519, 0.049993, 0.046987, 0.060242, 0.060899, 0.043769, 0.034036, 0.031942, 0.032395, 0.030383, 0.028779, 0.021595, 0.020306, 0.000000, 0.017844, 0.032797, 0.030589, 0.035253, 0.030820, 0.029029, 0.032808, 0.035748, 0.036530, 0.045163, 0.045472, 0.044694, 0.047442, 0.055395, 0.053106, 0.055122, 0.060495, 0.064599, 0.063701, 0.066688, 0.068827, 0.074492, 0.073843, 0.085741, 0.082118, 0.085197, 0.086770, 0.083677, 0.093027, 0.100202, 0.100709, 0.107606, 0.106787, 0.116950, 0.114421, 0.131035, 0.142708, 0.147779, 0.145490, 0.161485, 0.157688, 0.161332, 0.178819, 0.167347, 0.166246),
  lb3_m_marg  = c(0.204188, 0.183717, 0.176226, 0.170227, 0.168143, 0.147105, 0.126356, 0.126670, 0.110637, 0.106737, 0.081772, 0.090690, 0.087922, 0.093718, 0.080149, 0.076889, 0.065990, 0.056600, 0.054057, 0.050632, 0.041803, 0.048767, 0.044635, 0.042490, 0.043518, 0.038620, 0.032599, 0.031370, 0.019736, 0.016614, 0.014485, 0.016387, 0.021253, 0.020875, 0.020939, 0.015160, 0.023007, 0.016717, 0.010531, 0.011771, 0.006195, 0.006921, 0.013177, 0.003739, -0.002601, 0.000000, 0.006592, 0.012275, 0.014300, 0.012093, 0.006353, -0.006606, -0.008042, -0.002023, -0.001049, 0.007513, 0.001704, 0.002619, 0.007329, 0.010643, 0.009931, 0.008074, 0.007360, 0.003090, 0.005268, 0.003453, 0.012089, 0.015049, 0.013617, 0.023060, 0.020604, 0.023348, 0.024177, 0.013615, 0.021607, 0.020949, 0.028703, 0.032380, 0.029375, 0.030067, 0.022090, 0.022895, 0.017437, 0.023246, 0.027492, 0.031794, 0.042390, 0.039112, 0.032353, 0.051635, 0.045744)
)

# ── fig4 (levels & first-differences, by gender) ─────────────────────────────
fig4_all_lvl <- data.frame(
  p            = 5:95,
  b4_all_marg  = c(0.197804, 0.216479, 0.236255, 0.236619, 0.245629, 0.233043, 0.210666, 0.195925, 0.193196, 0.171771, 0.161731, 0.150753, 0.146552, 0.154258, 0.140621, 0.132685, 0.116945, 0.101283, 0.091457, 0.092238, 0.090142, 0.066638, 0.060835, 0.070013, 0.065165, 0.065790, 0.051209, 0.055803, 0.044396, 0.043556, 0.040738, 0.033988, 0.032669, 0.032173, 0.037025, 0.038023, 0.023608, 0.021383, 0.026274, 0.019028, 0.009331, 0.013042, 0.014276, 0.007743, 0.006588, 0.000000, -0.000478, 0.010975, 0.003475, 0.013641, 0.010093, 0.005909, 0.007430, 0.000608, -0.000975, -0.003440, -0.011275, -0.000990, -0.005882, -0.010632, -0.004845, -0.005790, -0.007608, -0.004225, -0.012048, -0.014536, -0.018137, -0.015508, -0.015842, -0.016343, -0.027758, -0.019451, -0.020853, -0.023565, -0.025150, -0.022454, -0.030660, -0.038096, -0.043007, -0.036625, -0.031255, -0.027510, -0.020783, -0.037642, -0.033914, -0.026069, -0.011819, 0.010175, 0.016978, 0.031123, 0.059110),
  ub4_all_marg = c(0.249818, 0.268090, 0.292156, 0.295739, 0.312363, 0.312429, 0.284480, 0.272720, 0.278743, 0.244456, 0.228505, 0.218566, 0.223010, 0.232226, 0.227783, 0.220039, 0.198004, 0.177220, 0.163134, 0.166481, 0.161044, 0.126123, 0.123716, 0.136753, 0.125157, 0.120148, 0.101568, 0.106918, 0.088433, 0.084324, 0.081627, 0.064414, 0.061034, 0.064062, 0.079037, 0.082837, 0.055729, 0.045120, 0.059065, 0.043861, 0.031514, 0.034124, 0.032856, 0.020042, 0.019775, 0.000000, 0.004777, 0.021835, 0.013308, 0.025782, 0.027248, 0.016303, 0.019869, 0.014239, 0.014945, 0.011698, 0.004929, 0.012295, 0.012791, 0.008876, 0.017939, 0.018501, 0.017104, 0.019883, 0.011919, 0.008660, 0.005839, 0.011970, 0.010625, 0.010370, -0.000868, 0.009253, 0.004672, 0.006810, 0.003143, 0.008910, 0.001320, -0.002060, -0.008921, -0.001872, 0.002972, 0.012969, 0.021707, 0.003806, 0.015118, 0.024212, 0.049426, 0.069836, 0.068562, 0.094623, 0.123823),
  lb4_all_marg = c(0.145789, 0.164868, 0.180355, 0.177499, 0.178895, 0.153658, 0.136852, 0.119131, 0.107649, 0.099086, 0.094956, 0.082941, 0.070095, 0.076290, 0.053460, 0.045331, 0.035885, 0.025347, 0.019781, 0.017994, 0.019241, 0.007153, -0.002046, 0.003274, 0.005173, 0.011431, 0.000851, 0.004688, 0.000359, 0.002787, -0.000150, 0.003562, 0.004304, 0.000285, -0.004986, -0.006791, -0.008512, -0.002353, -0.006517, -0.005804, -0.012851, -0.008039, -0.004303, -0.004556, -0.006600, 0.000000, -0.005733, 0.000116, -0.006357, 0.001500, -0.007062, -0.004485, -0.005009, -0.013022, -0.016894, -0.018578, -0.027478, -0.014275, -0.024555, -0.030141, -0.027629, -0.030081, -0.032320, -0.028333, -0.036014, -0.037731, -0.042113, -0.042987, -0.042310, -0.043057, -0.054648, -0.048156, -0.046379, -0.053939, -0.053443, -0.053818, -0.062640, -0.074132, -0.077092, -0.071377, -0.065482, -0.067989, -0.063272, -0.079089, -0.082946, -0.076349, -0.073063, -0.049487, -0.034607, -0.032377, -0.005602)
)

fig4_all_fd <- data.frame(
  p            = 5:95,
  b8_all_marg  = c(0.178439, 0.177953, 0.099920, 0.110767, 0.130795, 0.144986, 0.114426, 0.096347, 0.070280, 0.027607, 0.052423, 0.064358, 0.061762, 0.032001, 0.038130, 0.060793, 0.067036, 0.068545, 0.035823, 0.063534, 0.054443, 0.027378, 0.021129, 0.016953, 0.028074, 0.008408, 0.009517, 0.020274, 0.043546, 0.030430, 0.022848, 0.010517, 0.002193, -0.014034, 0.017366, 0.029190, 0.014243, 0.003470, 0.013171, 0.023885, 0.002290, 0.024289, 0.025287, 0.018561, 0.008461, 0.000000, -0.002698, 0.014803, -0.002854, 0.024555, 0.014772, -0.003424, -0.007969, 0.013604, 0.008585, 0.011077, 0.011888, 0.007526, 0.001280, -0.021848, -0.009143, -0.006848, 0.004356, 0.010589, 0.012135, 0.005381, 0.021109, 0.008947, 0.000555, 0.009203, -0.003747, 0.016438, 0.005284, -0.014473, 0.003993, 0.020286, -0.004220, 0.012189, -0.004854, 0.005086, -0.006551, -0.008531, 0.005524, -0.009651, 0.008653, 0.022415, 0.013116, 0.007374, -0.008871, -0.001279, 0.020957),
  ub8_all_marg = c(0.245165, 0.221088, 0.141875, 0.151453, 0.186294, 0.213315, 0.155023, 0.133343, 0.111622, 0.070891, 0.095039, 0.107211, 0.108050, 0.068030, 0.074010, 0.098122, 0.109726, 0.116017, 0.077663, 0.125515, 0.100986, 0.077221, 0.064167, 0.064085, 0.076591, 0.035896, 0.041367, 0.058199, 0.092658, 0.070232, 0.056615, 0.046773, 0.023667, 0.005754, 0.065754, 0.081101, 0.045514, 0.047392, 0.050675, 0.048303, 0.034222, 0.060462, 0.072148, 0.050809, 0.053774, 0.000000, 0.007935, 0.042308, 0.020567, 0.058601, 0.044464, 0.019168, 0.014663, 0.033661, 0.039443, 0.036067, 0.038049, 0.029994, 0.025496, 0.001449, 0.015251, 0.020643, 0.020922, 0.026593, 0.030100, 0.026313, 0.042996, 0.030185, 0.025347, 0.038460, 0.024905, 0.038815, 0.030042, 0.009808, 0.033249, 0.043903, 0.024636, 0.040451, 0.032499, 0.036200, 0.031847, 0.025258, 0.050225, 0.025304, 0.038306, 0.059284, 0.054401, 0.057083, 0.043392, 0.065673, 0.103537),
  lb8_all_marg = c(0.111714, 0.134817, 0.057965, 0.070081, 0.075296, 0.076656, 0.073828, 0.059350, 0.028937, -0.015678, 0.009807, 0.021504, 0.015474, -0.004028, 0.002251, 0.023465, 0.024346, 0.021073, -0.006017, 0.001552, 0.007900, -0.022465, -0.021909, -0.030179, -0.020444, -0.019080, -0.022334, -0.017652, -0.005566, -0.009373, -0.010918, -0.025740, -0.019282, -0.033823, -0.031022, -0.022722, -0.017029, -0.040453, -0.024333, -0.000534, -0.029641, -0.011884, -0.021573, -0.013687, -0.036852, 0.000000, -0.013332, -0.012702, -0.026275, -0.009490, -0.014920, -0.026017, -0.030601, -0.006454, -0.022272, -0.013913, -0.014274, -0.014941, -0.022936, -0.045144, -0.033536, -0.034339, -0.012210, -0.005415, -0.005830, -0.015552, -0.000779, -0.012291, -0.024237, -0.020054, -0.032399, -0.005939, -0.019474, -0.038754, -0.025263, -0.003332, -0.033076, -0.016072, -0.042207, -0.026028, -0.044950, -0.042320, -0.039177, -0.044606, -0.021000, -0.014455, -0.028169, -0.042335, -0.061134, -0.068232, -0.061624)
)

fig4_f_lvl <- data.frame(
  p           = 5:95,
  b4_f_marg   = c(0.138367, 0.188878, 0.241938, 0.263725, 0.286199, 0.274397, 0.277164, 0.270596, 0.256694, 0.249627, 0.234222, 0.207037, 0.192307, 0.193495, 0.187083, 0.187572, 0.170641, 0.156106, 0.145600, 0.124444, 0.112677, 0.106495, 0.088527, 0.086108, 0.069726, 0.068541, 0.058637, 0.051458, 0.041448, 0.042474, 0.038659, 0.027505, 0.028996, 0.027366, 0.029106, 0.030028, 0.040396, 0.047042, 0.042434, 0.025087, 0.021884, 0.016454, 0.019007, 0.006448, 0.011690, 0.000000, -0.007276, -0.000819, -0.001829, -0.000609, -0.004553, -0.000089, 0.008553, 0.014962, 0.012672, 0.010717, 0.000033, 0.010950, 0.004400, 0.004138, 0.008538, 0.012162, 0.008422, -0.003171, 0.009218, 0.002278, -0.006026, -0.015797, -0.009502, -0.015612, -0.011445, -0.005074, -0.017737, -0.012799, -0.022044, -0.029005, -0.038930, -0.034115, -0.034020, -0.031699, -0.043101, -0.048178, -0.055031, -0.054603, -0.048811, -0.052775, -0.060365, -0.068236, -0.061684, -0.035493, -0.049707),
  ub4_f_marg  = c(0.220496, 0.263783, 0.303006, 0.329057, 0.355811, 0.337400, 0.342955, 0.332994, 0.325162, 0.332871, 0.317177, 0.271258, 0.256571, 0.265386, 0.260390, 0.278608, 0.254746, 0.238240, 0.225093, 0.201511, 0.184386, 0.174775, 0.149045, 0.151043, 0.126944, 0.131600, 0.111683, 0.106924, 0.090558, 0.084356, 0.081054, 0.056797, 0.065291, 0.061431, 0.053467, 0.056647, 0.068093, 0.078730, 0.068909, 0.051125, 0.046352, 0.033807, 0.031971, 0.017957, 0.023942, 0.000000, 0.006599, 0.011041, 0.011351, 0.021367, 0.010074, 0.018293, 0.031681, 0.039304, 0.035991, 0.038995, 0.025655, 0.038596, 0.033285, 0.032956, 0.036011, 0.043420, 0.035297, 0.031151, 0.044650, 0.038908, 0.033077, 0.025119, 0.032763, 0.029718, 0.030810, 0.038003, 0.031898, 0.038657, 0.030393, 0.024862, 0.020032, 0.026694, 0.029037, 0.037254, 0.023866, 0.021365, 0.008917, 0.008649, 0.012650, 0.007826, -0.003511, -0.008304, 0.012870, 0.038858, 0.026844),
  lb4_f_marg  = c(0.056238, 0.113974, 0.180870, 0.198393, 0.216587, 0.211393, 0.211372, 0.208198, 0.188226, 0.166383, 0.151268, 0.142816, 0.128044, 0.121604, 0.113776, 0.096536, 0.086536, 0.073973, 0.066107, 0.047376, 0.040969, 0.038215, 0.028009, 0.021173, 0.012509, 0.005482, 0.005591, -0.004008, -0.007663, 0.000591, -0.003736, -0.001788, -0.007298, -0.006698, 0.004745, 0.003409, 0.012699, 0.015354, 0.015959, -0.000950, -0.002584, -0.000899, 0.006043, -0.005061, -0.000562, 0.000000, -0.021151, -0.012680, -0.015009, -0.022586, -0.019180, -0.018471, -0.014574, -0.009380, -0.010647, -0.017561, -0.025588, -0.016696, -0.024486, -0.024680, -0.018935, -0.019095, -0.018452, -0.037492, -0.026215, -0.034353, -0.045128, -0.056712, -0.051766, -0.060942, -0.053700, -0.048151, -0.067371, -0.064255, -0.074481, -0.082873, -0.097892, -0.094923, -0.097076, -0.100651, -0.110068, -0.117721, -0.118978, -0.117855, -0.110273, -0.113375, -0.117220, -0.128167, -0.136238, -0.109844, -0.126257)
)

fig4_f_fd <- data.frame(
  p           = 5:95,
  b8_f_marg   = c(0.256202, 0.229689, 0.246077, 0.152903, 0.141090, 0.135843, 0.145840, 0.176320, 0.145899, 0.118050, 0.101142, 0.060861, 0.061242, 0.076277, 0.074135, 0.078188, 0.072879, 0.078802, 0.081098, 0.096087, 0.084265, 0.084612, 0.079471, 0.079105, 0.056417, 0.055213, 0.050565, 0.039628, 0.033771, 0.034227, 0.022754, 0.034051, 0.033712, 0.036064, 0.024672, 0.019327, 0.032669, 0.014258, 0.016579, 0.006420, 0.022098, 0.015914, 0.016941, 0.008664, 0.016471, 0.000000, 0.014443, 0.032483, 0.016074, 0.018521, 0.013369, 0.005982, 0.020486, 0.011833, 0.000162, -0.010367, -0.011091, -0.008473, 0.015179, 0.003180, 0.005465, 0.015853, 0.009065, -0.007803, 0.004519, 0.001711, 0.005434, -0.014162, 0.004237, -0.020373, 0.008658, 0.014599, -0.002083, 0.018492, 0.013737, 0.004021, -0.012519, -0.025220, -0.006202, -0.020584, -0.003804, 0.000660, -0.008314, -0.029359, -0.043030, -0.028612, -0.015015, 0.009410, 0.011234, -0.007422, -0.043264),
  ub8_f_marg  = c(0.313793, 0.288134, 0.324864, 0.198689, 0.205190, 0.183287, 0.191325, 0.226664, 0.191310, 0.166870, 0.135919, 0.112911, 0.103108, 0.112830, 0.110763, 0.112484, 0.111517, 0.121797, 0.124817, 0.149231, 0.125951, 0.131186, 0.119278, 0.123469, 0.095991, 0.098084, 0.082209, 0.078765, 0.071374, 0.070788, 0.053927, 0.060795, 0.071066, 0.083080, 0.067606, 0.072628, 0.079014, 0.051947, 0.050720, 0.035864, 0.058393, 0.045821, 0.051515, 0.037616, 0.047152, 0.000000, 0.049945, 0.059707, 0.052832, 0.060668, 0.056764, 0.044409, 0.069062, 0.056383, 0.037862, 0.025444, 0.020224, 0.034021, 0.058310, 0.040797, 0.048766, 0.062589, 0.049957, 0.035605, 0.052360, 0.059350, 0.049500, 0.030137, 0.048073, 0.027882, 0.053540, 0.065379, 0.045809, 0.061315, 0.058784, 0.060089, 0.049724, 0.031207, 0.048653, 0.029980, 0.047805, 0.050271, 0.047348, 0.033768, 0.007811, 0.031536, 0.051951, 0.084297, 0.078853, 0.062281, 0.045586),
  lb8_f_marg  = c(0.198610, 0.171244, 0.167290, 0.107117, 0.076991, 0.088400, 0.100356, 0.125976, 0.100488, 0.069229, 0.066365, 0.008811, 0.019377, 0.039724, 0.037507, 0.043891, 0.034241, 0.035807, 0.037379, 0.042943, 0.042578, 0.038038, 0.039664, 0.034741, 0.016842, 0.012343, 0.018921, 0.000491, -0.003832, -0.002334, -0.008419, 0.007307, -0.003641, -0.010953, -0.018261, -0.033974, -0.013675, -0.023431, -0.017562, -0.023024, -0.014196, -0.013993, -0.017633, -0.020288, -0.014210, 0.000000, -0.021059, 0.005259, -0.020684, -0.023625, -0.030025, -0.032444, -0.028091, -0.032716, -0.037537, -0.046178, -0.042407, -0.050967, -0.027951, -0.034437, -0.037836, -0.030883, -0.031826, -0.051211, -0.043321, -0.055928, -0.038633, -0.058461, -0.039599, -0.068628, -0.036223, -0.036182, -0.049975, -0.024331, -0.031310, -0.052047, -0.074762, -0.081647, -0.061058, -0.071147, -0.055413, -0.048951, -0.063977, -0.092487, -0.093871, -0.088760, -0.081981, -0.065478, -0.056384, -0.077125, -0.132114)
)

fig4_m_lvl <- data.frame(
  p           = 5:95,
  b4_m_marg   = c(0.176786, 0.164053, 0.185503, 0.173472, 0.168887, 0.148012, 0.129332, 0.135625, 0.116896, 0.115015, 0.092902, 0.105000, 0.106808, 0.106063, 0.088634, 0.082788, 0.078764, 0.073758, 0.070635, 0.060923, 0.061669, 0.069573, 0.061589, 0.052133, 0.052658, 0.047634, 0.038477, 0.035985, 0.024212, 0.022001, 0.021777, 0.023000, 0.020808, 0.022075, 0.019676, 0.025173, 0.027715, 0.019120, 0.009232, 0.008737, 0.004534, 0.001097, 0.003643, -0.005569, -0.000389, 0.000000, 0.004282, 0.003722, -0.003715, -0.008028, -0.014394, -0.020420, -0.026386, -0.021573, -0.020655, -0.012343, -0.022434, -0.021483, -0.016188, -0.017259, -0.018423, -0.025420, -0.032181, -0.031027, -0.035806, -0.040484, -0.035693, -0.034197, -0.040044, -0.030278, -0.036618, -0.036546, -0.040857, -0.052651, -0.047215, -0.050301, -0.042735, -0.037114, -0.038217, -0.038080, -0.044316, -0.037875, -0.036573, -0.032597, -0.019352, 0.001047, 0.008228, 0.013662, 0.018740, 0.033559, 0.027428),
  ub4_m_marg  = c(0.250001, 0.218920, 0.242762, 0.237283, 0.246787, 0.214333, 0.190648, 0.199848, 0.182967, 0.180355, 0.153916, 0.170371, 0.178536, 0.182079, 0.159855, 0.148585, 0.139725, 0.141724, 0.138221, 0.117006, 0.116213, 0.129408, 0.116670, 0.101551, 0.102556, 0.101285, 0.074085, 0.072768, 0.053966, 0.053802, 0.049203, 0.056327, 0.058331, 0.056184, 0.046801, 0.068007, 0.059791, 0.041234, 0.027771, 0.018414, 0.016819, 0.012163, 0.013063, 0.001777, 0.010306, 0.000000, 0.010809, 0.015955, 0.006157, 0.007536, 0.002168, 0.001733, 0.002524, 0.004399, 0.006409, 0.010811, 0.006257, 0.007824, 0.008252, 0.008742, 0.006425, 0.001115, -0.003887, 0.001236, -0.004426, -0.005075, -0.004770, -0.001582, -0.007731, 0.001486, -0.003490, -0.003144, -0.006681, -0.012276, -0.005262, -0.004161, 0.000139, 0.007735, 0.008142, 0.013147, 0.003409, 0.022471, 0.033156, 0.041713, 0.043517, 0.069593, 0.069435, 0.074492, 0.094257, 0.100461, 0.092281),
  lb4_m_marg  = c(0.103570, 0.109186, 0.128244, 0.109662, 0.090987, 0.081692, 0.068017, 0.071401, 0.050825, 0.049676, 0.031889, 0.039629, 0.035080, 0.030046, 0.017414, 0.016991, 0.017803, 0.005792, 0.003048, 0.004840, 0.007125, 0.009738, 0.006509, 0.002714, 0.002760, -0.006016, 0.002869, -0.000798, -0.005541, -0.009800, -0.005648, -0.010326, -0.016715, -0.012034, -0.007449, -0.017661, -0.004360, -0.002993, -0.009306, -0.000939, -0.007751, -0.009969, -0.005776, -0.012914, -0.011083, 0.000000, -0.002245, -0.008511, -0.013586, -0.023592, -0.030956, -0.042573, -0.055297, -0.047546, -0.047719, -0.035497, -0.051126, -0.050790, -0.040628, -0.043260, -0.043270, -0.051955, -0.060475, -0.063290, -0.067187, -0.075893, -0.066617, -0.066812, -0.072357, -0.062043, -0.069746, -0.069947, -0.075034, -0.093026, -0.089167, -0.096441, -0.085608, -0.081962, -0.084577, -0.089306, -0.092041, -0.098222, -0.106303, -0.106906, -0.082222, -0.067498, -0.052979, -0.047168, -0.056776, -0.033342, -0.037424)
)

fig4_m_fd <- data.frame(
  p           = 5:95,
  b8_m_marg   = c(0.101034, 0.073602, 0.083125, 0.082763, 0.107915, 0.062476, 0.013293, 0.013619, 0.022908, 0.058629, -0.006642, -0.010733, 0.001926, 0.013898, 0.028836, 0.015607, 0.027971, 0.024223, 0.017966, 0.001172, 0.001784, 0.016357, 0.012561, -0.015607, 0.016389, 0.012424, -0.000055, -0.017653, -0.001148, 0.001062, -0.008597, 0.020231, -0.000288, -0.001670, -0.003436, 0.018966, 0.023441, 0.011092, 0.012043, -0.009702, 0.007430, 0.011372, 0.014586, 0.001179, 0.004801, 0.000000, 0.013201, 0.004723, -0.006042, -0.010593, -0.020367, -0.005755, -0.017827, 0.004657, -0.010380, -0.010845, -0.014772, 0.000849, -0.009110, 0.009154, 0.001232, 0.007417, -0.002871, 0.001687, 0.002201, -0.007490, 0.003476, 0.002876, 0.004467, 0.008432, -0.005707, 0.004519, -0.000992, -0.003437, 0.004859, -0.009172, -0.000434, 0.009392, 0.001089, -0.013595, -0.013180, 0.002065, 0.009045, 0.024554, 0.025115, 0.013933, -0.021285, -0.020338, -0.010185, 0.025599, 0.004241),
  ub8_m_marg  = c(0.157584, 0.125425, 0.149046, 0.132984, 0.171779, 0.117429, 0.062866, 0.068378, 0.071311, 0.114879, 0.037797, 0.036125, 0.048651, 0.061134, 0.077653, 0.067943, 0.080545, 0.092725, 0.079166, 0.045189, 0.044055, 0.070392, 0.059173, 0.024855, 0.062305, 0.062633, 0.035324, 0.010815, 0.035775, 0.039598, 0.021766, 0.051479, 0.038279, 0.026616, 0.026537, 0.063071, 0.059894, 0.035048, 0.047042, 0.016904, 0.039207, 0.036367, 0.032612, 0.015649, 0.026830, 0.000000, 0.033085, 0.030337, 0.015640, 0.013246, 0.004867, 0.018114, 0.014282, 0.030715, 0.020396, 0.007335, 0.010121, 0.029952, 0.023758, 0.034767, 0.031807, 0.036608, 0.028045, 0.034649, 0.032093, 0.027929, 0.034900, 0.033910, 0.034337, 0.034638, 0.017639, 0.033901, 0.025040, 0.027027, 0.037039, 0.026689, 0.029515, 0.034011, 0.046309, 0.019539, 0.016726, 0.034881, 0.060808, 0.080986, 0.066763, 0.063305, 0.042778, 0.046611, 0.117504, 0.112920, 0.073719),
  lb8_m_marg  = c(0.044485, 0.021780, 0.017204, 0.032542, 0.044050, 0.007524, -0.036280, -0.041141, -0.025495, 0.002378, -0.051081, -0.057590, -0.044798, -0.033337, -0.019981, -0.036729, -0.024603, -0.044279, -0.043234, -0.042845, -0.040486, -0.037678, -0.034050, -0.056068, -0.029528, -0.037785, -0.035434, -0.046122, -0.038071, -0.037473, -0.038960, -0.011016, -0.038854, -0.029956, -0.033409, -0.025139, -0.013012, -0.012863, -0.022956, -0.036309, -0.024347, -0.013623, -0.003440, -0.013291, -0.017227, 0.000000, -0.006682, -0.020890, -0.027724, -0.034433, -0.045601, -0.029624, -0.049937, -0.021402, -0.041157, -0.029026, -0.039666, -0.028253, -0.041978, -0.016460, -0.029343, -0.021774, -0.033787, -0.031275, -0.027691, -0.042908, -0.027948, -0.028158, -0.025403, -0.017774, -0.029054, -0.024862, -0.027025, -0.033900, -0.027321, -0.045033, -0.030384, -0.015227, -0.044131, -0.046730, -0.043087, -0.030750, -0.042717, -0.031878, -0.016532, -0.035438, -0.085348, -0.087287, -0.137875, -0.061721, -0.065238)
)

# ── fig5 ─────────────────────────────────────────────────────────────────────
# Marginal effects — OLS cross-section (b1), 1979–2024
fig5_all <- data.frame(
  p            = 5:95,
  b1_all_marg  = c(0.404705, 0.389805, 0.362404, 0.339879, 0.319080, 0.292785, 0.273154, 0.246916, 0.225343, 0.208538, 0.189643, 0.182857, 0.171612, 0.163092, 0.147589, 0.140490, 0.133298, 0.121875, 0.110518, 0.109044, 0.103261, 0.094223, 0.083038, 0.080135, 0.072739, 0.068183, 0.061189, 0.061444, 0.055640, 0.047442, 0.045432, 0.042691, 0.038173, 0.032589, 0.030248, 0.030420, 0.025347, 0.020228, 0.022393, 0.018336, 0.017533, 0.015639, 0.009810, 0.006850, 0.006617, 0.000000, -0.000281, 0.002593, 0.003889, 0.004709, 0.002097, 0.003710, 0.001800, 0.001440, 0.000007, 0.001917, 0.001778, 0.001432, 0.002536, 0.001265, 0.004804, 0.007069, 0.013735, 0.015167, 0.016867, 0.020108, 0.026050, 0.030070, 0.031992, 0.035587, 0.039344, 0.042067, 0.046678, 0.050637, 0.055247, 0.058156, 0.058797, 0.058684, 0.062952, 0.065729, 0.068298, 0.068971, 0.072589, 0.066086, 0.060287, 0.063882, 0.064205, 0.060414, 0.056066, 0.054086, 0.056963),
  ub1_all_marg = c(0.469177, 0.451848, 0.424189, 0.400847, 0.374007, 0.345564, 0.326872, 0.303590, 0.284562, 0.267365, 0.250259, 0.239220, 0.225019, 0.215068, 0.200722, 0.192717, 0.182979, 0.169820, 0.156934, 0.151316, 0.146947, 0.138067, 0.123666, 0.118204, 0.108905, 0.104547, 0.094655, 0.092149, 0.085316, 0.077683, 0.072546, 0.068551, 0.060743, 0.054139, 0.049893, 0.047684, 0.040573, 0.033836, 0.031624, 0.026247, 0.024496, 0.020981, 0.013592, 0.010318, 0.010975, 0.000000, 0.002482, 0.008677, 0.012917, 0.016662, 0.015208, 0.018731, 0.017978, 0.015328, 0.016951, 0.021762, 0.021333, 0.022212, 0.028173, 0.027756, 0.030840, 0.036777, 0.045636, 0.048064, 0.053620, 0.057651, 0.066366, 0.073748, 0.077072, 0.081238, 0.087849, 0.091286, 0.096396, 0.102158, 0.109948, 0.112583, 0.112895, 0.111807, 0.119878, 0.126679, 0.129226, 0.129531, 0.137733, 0.126103, 0.120634, 0.126979, 0.129197, 0.125513, 0.121217, 0.120269, 0.126168),
  lb1_all_marg = c(0.340234, 0.327762, 0.300618, 0.278910, 0.264152, 0.240005, 0.219436, 0.190242, 0.166123, 0.149711, 0.129028, 0.126494, 0.118204, 0.111117, 0.094457, 0.088263, 0.083617, 0.073931, 0.064101, 0.066773, 0.059574, 0.050380, 0.042410, 0.042066, 0.036574, 0.031820, 0.027723, 0.030739, 0.025964, 0.017201, 0.018318, 0.016830, 0.015602, 0.011039, 0.010603, 0.013156, 0.010121, 0.006620, 0.013162, 0.010424, 0.010571, 0.010298, 0.006029, 0.003382, 0.002260, 0.000000, -0.003043, -0.003491, -0.005140, -0.007244, -0.011014, -0.011311, -0.014379, -0.012448, -0.016938, -0.017928, -0.017777, -0.019347, -0.023100, -0.025226, -0.021231, -0.022638, -0.018165, -0.017731, -0.019885, -0.017435, -0.014266, -0.013609, -0.013088, -0.010064, -0.009162, -0.007152, -0.003041, -0.000884, 0.000547, 0.003729, 0.004699, 0.005562, 0.006027, 0.004779, 0.007370, 0.008412, 0.007444, 0.006069, -0.000059, 0.000785, -0.000786, -0.004686, -0.009085, -0.012096, -0.012241)
)

fig5_f <- data.frame(
  p           = 5:95,
  b1_f_marg   = c(0.426847, 0.436995, 0.439676, 0.420362, 0.398847, 0.381674, 0.360685, 0.340514, 0.314084, 0.288157, 0.267145, 0.245766, 0.224283, 0.213622, 0.203409, 0.191050, 0.172900, 0.162162, 0.148232, 0.135770, 0.129027, 0.122314, 0.114202, 0.105815, 0.095322, 0.088076, 0.078708, 0.073844, 0.070037, 0.066014, 0.058212, 0.055361, 0.048423, 0.043740, 0.042765, 0.036516, 0.033850, 0.029389, 0.030619, 0.028609, 0.020928, 0.017886, 0.016691, 0.011512, 0.003570, 0.000000, 0.000698, -0.002952, -0.003273, -0.002480, -0.001814, -0.003823, -0.005216, -0.005744, -0.009520, -0.005657, -0.008670, -0.007313, -0.007068, -0.006072, -0.007571, -0.005841, -0.007981, -0.007937, -0.004717, -0.005985, -0.004904, -0.008297, -0.006976, -0.003797, 0.000903, 0.003030, 0.001924, 0.006002, 0.004868, 0.003637, 0.005159, 0.011291, 0.012726, 0.011095, 0.011771, 0.015290, 0.019831, 0.020673, 0.023618, 0.021932, 0.021280, 0.018350, 0.011354, 0.007013, -0.007799),
  ub1_f_marg  = c(0.470805, 0.479852, 0.483386, 0.462149, 0.440326, 0.423551, 0.405850, 0.386271, 0.358065, 0.328892, 0.308131, 0.285630, 0.264031, 0.253276, 0.242591, 0.228645, 0.207701, 0.194982, 0.180173, 0.168514, 0.161946, 0.154318, 0.143803, 0.133561, 0.124230, 0.115293, 0.105751, 0.098232, 0.093248, 0.088469, 0.080343, 0.075955, 0.069747, 0.067501, 0.063932, 0.056160, 0.052682, 0.047688, 0.045952, 0.041229, 0.031818, 0.027975, 0.023544, 0.016500, 0.008567, 0.000000, 0.003566, 0.001243, 0.002037, 0.004120, 0.007328, 0.005177, 0.006312, 0.008165, 0.004189, 0.010955, 0.007895, 0.011217, 0.014187, 0.017503, 0.015424, 0.018714, 0.019007, 0.021413, 0.027823, 0.024523, 0.029516, 0.027013, 0.029878, 0.032955, 0.040265, 0.046276, 0.045491, 0.052190, 0.053966, 0.053486, 0.056688, 0.064313, 0.066161, 0.064040, 0.064502, 0.070970, 0.074706, 0.074799, 0.080907, 0.082952, 0.082491, 0.082968, 0.075243, 0.072313, 0.059538),
  lb1_f_marg  = c(0.382890, 0.394138, 0.395966, 0.378575, 0.357369, 0.339797, 0.315519, 0.294756, 0.270104, 0.247422, 0.226159, 0.205903, 0.184534, 0.173968, 0.164227, 0.153456, 0.138098, 0.129341, 0.116291, 0.103027, 0.096107, 0.090310, 0.084600, 0.078069, 0.066414, 0.060859, 0.051664, 0.049456, 0.046827, 0.043560, 0.036081, 0.034767, 0.027099, 0.019979, 0.021598, 0.016872, 0.015018, 0.011090, 0.015286, 0.015990, 0.010037, 0.007797, 0.009838, 0.006523, -0.001427, 0.000000, -0.002171, -0.007147, -0.008584, -0.009081, -0.010956, -0.012823, -0.016743, -0.019654, -0.023229, -0.022268, -0.025235, -0.025842, -0.028322, -0.029647, -0.030566, -0.030396, -0.034970, -0.037287, -0.037257, -0.036494, -0.039324, -0.043608, -0.043829, -0.040548, -0.038458, -0.040216, -0.041644, -0.040187, -0.044230, -0.046212, -0.046370, -0.041731, -0.040708, -0.041850, -0.040961, -0.040391, -0.035044, -0.033453, -0.033671, -0.039089, -0.039931, -0.046268, -0.052534, -0.058287, -0.075136)
)

fig5_m <- data.frame(
  p           = 5:95,
  b1_m_marg   = c(0.343036, 0.310519, 0.286801, 0.266513, 0.247281, 0.222638, 0.197600, 0.183430, 0.168543, 0.164346, 0.156086, 0.150729, 0.131547, 0.122062, 0.109718, 0.101449, 0.092425, 0.081521, 0.072771, 0.064631, 0.057190, 0.052604, 0.045420, 0.039825, 0.040932, 0.033711, 0.027779, 0.026749, 0.022106, 0.018559, 0.015021, 0.011226, 0.010501, 0.009127, 0.008595, 0.009731, 0.009072, 0.005782, 0.004002, 0.000728, 0.001392, 0.005499, 0.007649, 0.002702, 0.000745, 0.000000, 0.000779, 0.007298, 0.009247, 0.012888, 0.010076, 0.010392, 0.012906, 0.016595, 0.018999, 0.022897, 0.026796, 0.030699, 0.033776, 0.039117, 0.040080, 0.046967, 0.053785, 0.056541, 0.059583, 0.063878, 0.070698, 0.077890, 0.079564, 0.089118, 0.091210, 0.096515, 0.100259, 0.102357, 0.102535, 0.102797, 0.109151, 0.113892, 0.114481, 0.113396, 0.118288, 0.116332, 0.118246, 0.121602, 0.124067, 0.125878, 0.125048, 0.125477, 0.128446, 0.132308, 0.118385),
  ub1_m_marg  = c(0.430626, 0.395794, 0.371183, 0.346312, 0.320947, 0.295870, 0.271772, 0.256462, 0.243368, 0.239870, 0.228038, 0.219024, 0.199618, 0.185936, 0.171467, 0.161825, 0.151608, 0.134788, 0.124573, 0.115215, 0.105814, 0.095856, 0.088291, 0.082029, 0.079491, 0.071136, 0.065656, 0.059483, 0.053201, 0.048099, 0.043109, 0.038802, 0.035405, 0.032616, 0.029749, 0.025942, 0.025075, 0.021185, 0.016829, 0.015841, 0.014330, 0.014832, 0.014052, 0.008532, 0.004152, 0.000000, 0.005243, 0.012791, 0.016101, 0.021172, 0.018862, 0.020662, 0.024639, 0.031042, 0.035111, 0.041637, 0.047562, 0.051815, 0.058600, 0.066344, 0.070269, 0.079360, 0.088267, 0.093225, 0.099652, 0.105779, 0.114406, 0.122492, 0.127458, 0.140066, 0.142784, 0.151596, 0.157961, 0.159268, 0.159643, 0.161181, 0.171526, 0.178019, 0.179070, 0.177782, 0.187970, 0.184126, 0.187370, 0.191161, 0.199376, 0.203777, 0.201755, 0.203010, 0.210084, 0.214779, 0.205325),
  lb1_m_marg  = c(0.255446, 0.225243, 0.202419, 0.186714, 0.173616, 0.149407, 0.123428, 0.110399, 0.093718, 0.088822, 0.084133, 0.082433, 0.063477, 0.058188, 0.047969, 0.041073, 0.033243, 0.028254, 0.020969, 0.014046, 0.008567, 0.009352, 0.002549, -0.002378, 0.002373, -0.003713, -0.010099, -0.005985, -0.008990, -0.010981, -0.013067, -0.016350, -0.014403, -0.014361, -0.012558, -0.006480, -0.006930, -0.009621, -0.008825, -0.014385, -0.011545, -0.003834, 0.001245, -0.003127, -0.002661, 0.000000, -0.003686, 0.001806, 0.002393, 0.004604, 0.001289, 0.000122, 0.001174, 0.002149, 0.002888, 0.004157, 0.006031, 0.009583, 0.008953, 0.011889, 0.009891, 0.014573, 0.019303, 0.019857, 0.019513, 0.021978, 0.026990, 0.033287, 0.031669, 0.038170, 0.039637, 0.041434, 0.042557, 0.045446, 0.045426, 0.044414, 0.046776, 0.049765, 0.049892, 0.049011, 0.048606, 0.048537, 0.049122, 0.052044, 0.048758, 0.047978, 0.048341, 0.047943, 0.046807, 0.049837, 0.031445)
)


# =============================================================================
# FIGURE 2
# Share of workers at or below the minimum wage, by gender (1979–2024)
# =============================================================================

fig2_plot <- ggplot(fig2, aes(x = year)) +
  geom_line(aes(y = sharef,   color = "Female",             linetype = "Female"),   linewidth = 0.9) +
  geom_line(aes(y = sharem,   color = "Male",               linetype = "Male"),     linewidth = 0.9) +
  geom_line(aes(y = shareall, color = "Male/female pooled", linetype = "Male/female pooled"), linewidth = 0.7) +
  geom_point(aes(y = shareall, color = "Male/female pooled"), shape = 1, size = 1.5) +
  scale_x_continuous(
    breaks = c(1979, 1985, 1990, 1995, 2000, 2005, 2010, 2015, 2020, 2024),
    limits = c(1979, 2025)
  ) +
  scale_y_continuous(
    name   = "Share at or below the minimum",
    limits = c(0, 0.14),
    breaks = seq(0, 0.14, 0.02),
    labels = number_format(accuracy = 0.02)
  ) +
  scale_color_manual(
    name = NULL,
    values = c("Female" = "#D46A00", "Male" = "#8B1A1A", "Male/female pooled" = "#1F3E6E")
  ) +
  scale_linetype_manual(
    name = NULL,
    values = c("Female" = "dashed", "Male" = "dotted", "Male/female pooled" = "solid")
  ) +
  guides(color = guide_legend(nrow = 1), linetype = guide_legend(nrow = 1)) +
  labs(x = NULL) +
  stata_theme


# =============================================================================
# FIGURE 3 / 4 / 5 HELPER — percentile marginal-effect plots
# All use: y-axis -.2 to .7, breaks at .1; x-axis percentile 5–95
# =============================================================================

make_pct_plot <- function(df, b_col, ub_col, lb_col,
                          ylims   = c(-0.2, 0.7),
                          ybreaks = seq(-0.2, 0.7, 0.1)) {
  ggplot(df, aes(x = p)) +
    geom_line(aes(y = .data[[b_col]],  color = "Marginal effect"),
              linetype = "solid",  linewidth = 1.1) +
    geom_line(aes(y = .data[[ub_col]], color = "95% CI bounds"),
              linetype = "dashed", linewidth = 1.1) +
    geom_line(aes(y = .data[[lb_col]], color = "95% CI bounds"),
              linetype = "dashed", linewidth = 1.1) +
    geom_hline(yintercept = 0, linewidth = 0.4, color = "black") +
    scale_x_continuous(
      name   = "Percentile",
      breaks = seq(0, 100, 10),
      limits = c(5, 95)
    ) +
    scale_y_continuous(
      name   = "",
      limits = ylims,
      breaks = ybreaks,
      labels = number_format(accuracy = 0.1)
    ) +
    scale_color_manual(
      values = c("Marginal effect" = "#0000CD", "95% CI bounds" = "#8B1A1A")
    ) +
    stata_theme +
    theme(legend.position = "none")
}

# ── fig3 plots ────────────────────────────────────────────────────────────────
fig3_all_plot <- make_pct_plot(fig3_all, "b3_all_marg", "ub3_all_marg", "lb3_all_marg")
fig3_f_plot   <- make_pct_plot(fig3_f,   "b3_f_marg",   "ub3_f_marg",   "lb3_f_marg")
fig3_m_plot   <- make_pct_plot(fig3_m,   "b3_m_marg",   "ub3_m_marg",   "lb3_m_marg")

# ── fig4 plots ────────────────────────────────────────────────────────────────
fig4_all_lvl_plot <- make_pct_plot(fig4_all_lvl, "b4_all_marg", "ub4_all_marg", "lb4_all_marg")
fig4_all_fd_plot  <- make_pct_plot(fig4_all_fd,  "b8_all_marg", "ub8_all_marg", "lb8_all_marg")
fig4_f_lvl_plot   <- make_pct_plot(fig4_f_lvl,   "b4_f_marg",   "ub4_f_marg",   "lb4_f_marg")
fig4_f_fd_plot    <- make_pct_plot(fig4_f_fd,    "b8_f_marg",   "ub8_f_marg",   "lb8_f_marg")
fig4_m_lvl_plot   <- make_pct_plot(fig4_m_lvl,   "b4_m_marg",   "ub4_m_marg",   "lb4_m_marg")
fig4_m_fd_plot    <- make_pct_plot(fig4_m_fd,    "b8_m_marg",   "ub8_m_marg",   "lb8_m_marg")

# ── fig5 plots ────────────────────────────────────────────────────────────────
fig5_all_plot <- make_pct_plot(fig5_all, "b1_all_marg", "ub1_all_marg", "lb1_all_marg")
fig5_f_plot   <- make_pct_plot(fig5_f,   "b1_f_marg",   "ub1_f_marg",   "lb1_f_marg")
fig5_m_plot   <- make_pct_plot(fig5_m,   "b1_m_marg",   "ub1_m_marg",   "lb1_m_marg")
```

```{r,echo=FALSE,warning=FALSE,message=FALSE}
# =============================================================================
# R Code to Reproduce Stata .gph Figures — Batch 3
# Figures: fig6a (all/f/m), fig6b (all/f/m), fig8a, fig8b, fig9a, fig9b
# Generated from parsed Stata serset binary data
# =============================================================================

library(ggplot2)
library(scales)

# ── Shared theme (mimics Stata's stcolor scheme) ─────────────────────────────
stata_theme <- theme_bw() +
  theme(
    panel.background  = element_rect(fill = "white", color = "white"),
    plot.background   = element_rect(fill = "white", color = "white"),
    panel.border      = element_rect(color = "grey80"),
    panel.grid.major  = element_line(color = "white", linewidth = 0.4),
    panel.grid.minor  = element_blank(),
    legend.background = element_rect(fill = "white", color = NA),
    legend.key        = element_rect(fill = "white"),
    legend.position   = "bottom",
    legend.text       = element_text(size = 7),
    axis.text         = element_text(size = 7),
    axis.title        = element_text(size = 7),
    plot.margin       = margin(4, 6, 4, 6, "pt")
  )


# =============================================================================
# DATA
# =============================================================================

# ── fig6a: Mean log(p60)–log(p40) vs mean log(p50), 1979–2024, by state ──────
# 48 states (contiguous US + RI/DC region; AK excluded from data)
# x = mean log p50 (real wage level), y = mean log(p60/p40) (wage spread)

fig6a_all <- data.frame(
  abbrev = c('ME','NH','VT','MA','RI','CT','NY','NJ','PA','OH','IN','IL','MI','WI','MN','IA','MO','ND','SD','NE','KS','DE','MD','VA','WV','NC','SC','GA','FL','KY','TN','AL','MS','AR','LA','OK','TX','MT','ID','WY','CO','NM','AZ','UT','NV','WA','OR','CA'),
  y = c(0.27375564,0.24374224,0.30291486,0.28987169,0.30285662,0.32392797,0.33371270,0.29220727,0.28586110,0.27519423,0.31562361,0.31661606,0.27153271,0.28860563,0.26872164,0.29825372,0.26216978,0.24442276,0.26343116,0.28480569,0.30650142,0.31807134,0.33150283,0.31359461,0.27529579,0.26178125,0.29468334,0.28413436,0.28893721,0.27389723,0.30198401,0.28718767,0.25722307,0.31939298,0.28724816,0.31494007,0.29866159,0.28310317,0.29754889,0.30515009,0.31042078,0.30262733,0.29345161,0.28183001,0.30602312,0.29533970,0.34789741,0.28259543),
  x = c(2.08568549,1.97303653,2.19000936,2.04213047,2.23164558,2.11951327,2.21726727,2.04067492,2.01738644,1.95644784,2.08989859,2.08147430,2.01815557,2.09910536,1.93634963,1.95102751,1.88357747,1.82810485,1.89182401,1.94460237,2.05508280,2.19058180,2.08155560,1.89085317,1.89326119,1.88509130,1.94472575,1.90201735,1.89997542,1.87549448,1.87511933,1.78346217,1.79409730,1.89707696,1.89049673,1.92959201,1.88150203,1.88643062,1.97919226,2.09586477,1.90247929,1.97668207,1.97879934,1.97139311,2.15602469,2.05246544,2.12456822,2.02787948)
)

fig6a_f <- data.frame(
  abbrev = c('ME','NH','VT','MA','RI','CT','NY','NJ','PA','OH','IN','IL','MI','WI','MN','IA','MO','ND','SD','NE','KS','DE','MD','VA','WV','NC','SC','GA','FL','KY','TN','AL','MS','AR','LA','OK','TX','MT','ID','WY','CO','NM','AZ','UT','NV','WA','OR','CA'),
  y = c(0.24396661,0.24213174,0.29032829,0.25943279,0.28996229,0.31362262,0.31394643,0.27314124,0.27309531,0.23884413,0.28565362,0.28104365,0.24177733,0.25868031,0.24714704,0.25466627,0.22980012,0.21544006,0.24166909,0.25409675,0.27823377,0.30954498,0.30555981,0.28215048,0.24669564,0.24077405,0.27474189,0.26396656,0.26095882,0.25022721,0.26986459,0.26248065,0.24287662,0.29061911,0.26427901,0.29252616,0.24066287,0.24228211,0.24910238,0.27589941,0.28521255,0.26276353,0.23996200,0.23780537,0.27231872,0.25848842,0.31505787,0.24630713),
  x = c(1.93747330,1.88386703,2.06781054,1.92069125,2.07877541,2.00669789,2.07544351,1.88356030,1.86238480,1.79573119,1.94103146,1.90474057,1.86770046,1.97379911,1.80262566,1.81392908,1.74880314,1.72104490,1.77237046,1.80969882,1.92682493,2.08557105,1.94873142,1.69891655,1.79221451,1.76113975,1.83532417,1.80424619,1.75649405,1.76023877,1.71386659,1.64088356,1.68611908,1.71425831,1.75180185,1.81938493,1.72849083,1.74569213,1.75903904,1.96732175,1.76792920,1.86349928,1.79248452,1.85514414,1.99695313,1.90920365,2.02807641,1.91923368)
)

fig6a_m <- data.frame(
  abbrev = c('ME','NH','VT','MA','RI','CT','NY','NJ','PA','OH','IN','IL','MI','WI','MN','IA','MO','ND','SD','NE','KS','DE','MD','VA','WV','NC','SC','GA','FL','KY','TN','AL','MS','AR','LA','OK','TX','MT','ID','WY','CO','NM','AZ','UT','NV','WA','OR','CA'),
  y = c(0.27298045,0.24305719,0.29906395,0.27955249,0.27904883,0.32292029,0.32455018,0.27270442,0.26950788,0.26442245,0.31514719,0.29593962,0.24852403,0.28192443,0.25931677,0.29838195,0.26462445,0.24433149,0.26619655,0.28680423,0.29911542,0.31653374,0.33091995,0.30233693,0.28236350,0.26929086,0.31165260,0.29571450,0.27525640,0.27820405,0.29943427,0.27483130,0.26215464,0.30180818,0.28976482,0.32584557,0.28225583,0.28713903,0.27320084,0.30943099,0.31685486,0.30895025,0.28903753,0.30281910,0.28668410,0.27660531,0.35275149,0.30013755),
  x = c(2.20704651,2.04716468,2.29371667,2.14592099,2.34274840,2.21294808,2.33039713,2.15460014,2.13410282,2.08568549,2.21387100,2.21315408,2.13560057,2.20625639,2.04797292,2.08876085,1.99613380,1.92590725,1.99221992,2.05574536,2.16833353,2.27997541,2.19581747,2.02623653,1.98351347,1.99413538,2.04388595,1.98624730,2.01291800,1.98263443,2.00185609,1.90018511,1.89173400,2.03958011,2.00353003,2.01552629,2.02287221,2.00099826,2.12860513,2.20343971,2.00895691,2.07511640,2.11494350,2.08038139,2.27879715,2.16297531,2.21101046,2.14994574)
)

# ── fig6b: Trend log(p60)–log(p40) vs trend log(p50), 1979–2012, by state ────
fig6b_all <- data.frame(
  abbrev = c('ME','NH','VT','MA','RI','CT','NY','NJ','PA','OH','IN','IL','MI','WI','MN','IA','MO','ND','SD','NE','KS','DE','MD','VA','WV','NC','SC','GA','FL','KY','TN','AL','MS','AR','LA','OK','TX','MT','ID','WY','CO','NM','AZ','UT','NV','WA','OR','CA'),
  y = c(0.00192871,0.00114746,0.00288264,0.00170406,0.00255782,0.00173921,0.00246952,0.00130894,0.00023770,0.00014242,0.00151089,0.00022367,-0.00048703,0.00050492,-0.00019491,-0.00016974,-0.00086967,-0.00040988,0.00019863,0.00030707,0.00046914,0.00184294,0.00180207,-0.00143496,0.00217088,0.00146785,0.00135736,0.00096751,-0.00103691,0.00078386,-0.00047380,0.00010707,0.00110618,-0.00009422,-0.00004543,0.00056041,-0.00082778,0.00015604,-0.00108163,0.00004844,0.00001085,-0.00016782,0.00061093,-0.00014237,0.00095588,0.00006968,0.00154157,0.00046049),
  x = c(0.00775406,0.00851953,0.00822426,0.00712184,0.00528611,0.00420897,0.00530658,0.00405787,0.00169973,0.00370151,0.00268208,0.00011457,0.00358838,0.00578778,0.00407862,0.00478762,0.00752711,0.00822660,0.00632943,0.00343777,0.00357663,0.00581305,0.00767461,0.00305677,0.00679467,0.00728488,0.00625473,0.00672701,0.00359526,0.00603944,0.00654079,0.00567187,0.00735592,0.00334888,0.00226458,0.00387253,0.00366615,0.00401392,0.00234784,0.00507421,0.00375233,0.00392939,0.00349279,0.00119770,0.00350668,0.00307637,0.00225059,0.00228510)
)

fig6b_f <- data.frame(
  abbrev = c('ME','NH','VT','MA','RI','CT','NY','NJ','PA','OH','IN','IL','MI','WI','MN','IA','MO','ND','SD','NE','KS','DE','MD','VA','WV','NC','SC','GA','FL','KY','TN','AL','MS','AR','LA','OK','TX','MT','ID','WY','CO','NM','AZ','UT','NV','WA','OR','CA'),
  y = c(0.00299287,0.00187251,0.00426522,0.00288107,0.00377527,0.00281712,0.00374553,0.00243491,0.00150762,0.00149346,0.00257832,0.00126613,0.00115475,0.00215940,0.00079899,0.00104257,0.00049826,0.00124331,0.00143479,0.00133246,0.00139117,0.00238716,0.00251730,0.00042765,0.00291879,0.00162782,0.00232356,0.00181393,0.00064680,0.00201546,0.00199432,0.00158436,0.00263973,0.00141085,0.00008236,0.00127517,0.00102323,0.00077714,-0.00014816,0.00100704,0.00106656,0.00157266,0.00170224,0.00049057,0.00248675,0.00201267,0.00299288,0.00126124),
  x = c(0.01032828,0.01107578,0.01079065,0.01026915,0.00834129,0.00702664,0.00867863,0.00760453,0.00624764,0.00789106,0.00646596,0.00509600,0.00805279,0.00902341,0.00767106,0.00758031,0.01064626,0.01040025,0.00942117,0.00668433,0.00774198,0.00893518,0.01023640,0.00778714,0.00850656,0.00890708,0.00810355,0.00888781,0.00807095,0.00848490,0.01002506,0.00830048,0.00952915,0.00708457,0.00474417,0.00590858,0.00755414,0.00700520,0.00640170,0.00820641,0.00658556,0.00670211,0.00604519,0.00393799,0.00671150,0.00774594,0.00500142,0.00510320)
)

fig6b_m <- data.frame(
  abbrev = c('ME','NH','VT','MA','RI','CT','NY','NJ','PA','OH','IN','IL','MI','WI','MN','IA','MO','ND','SD','NE','KS','DE','MD','VA','WV','NC','SC','GA','FL','KY','TN','AL','MS','AR','LA','OK','TX','MT','ID','WY','CO','NM','AZ','UT','NV','WA','OR','CA'),
  y = c(0.00236701,0.00107000,0.00339404,0.00185499,0.00317116,0.00182059,0.00376141,0.00230620,0.00151444,0.00119262,0.00231303,0.00215793,0.00095488,0.00088992,0.00077642,-0.00015167,-0.00081554,-0.00024514,-0.00025051,0.00089014,0.00105792,0.00247631,0.00241450,-0.00092490,0.00246709,0.00120352,0.00126126,0.00099360,0.00014236,0.00093578,0.00008727,0.00042606,0.00086806,0.00067816,0.00051992,0.00072666,0.00043167,0.00022965,-0.00040772,0.00131468,-0.00062558,0.00032997,0.00175347,0.00033132,0.00298215,0.00254753,0.00187765,0.00007334),
  x = c(0.00634961,0.00709881,0.00647708,0.00497264,0.00333167,0.00232083,0.00328002,0.00214044,-0.00089529,0.00095536,-0.00013119,-0.00243865,0.00041336,0.00287052,0.00148297,0.00191353,0.00498894,0.00583089,0.00384319,0.00119839,0.00021089,0.00329437,0.00615086,0.00024057,0.00521121,0.00564355,0.00425646,0.00509745,0.00074267,0.00363033,0.00394510,0.00384544,0.00531772,0.00178116,0.00048331,0.00188511,0.00060299,0.00102044,-0.00001429,0.00222868,0.00172788,0.00125198,0.00200020,-0.00154464,0.00126263,-0.00014787,-0.00032925,-0.00072572)
)

# ── fig8: Actual vs counterfactual wage changes, 1979–1989, by percentile ─────
# yr_0 = Actual change
# yr_1 = Counterfactual: no state FE
# yr_2 = Counterfactual: state time trends
# yr_3 = Counterfactual: FD

fig8a <- data.frame(
  p    = 5:95,
  yr_0 = c(-0.27073258,-0.29865122,-0.30228090,-0.27171826,-0.24640048,-0.24640048,-0.23397791,-0.18577588,-0.20287037,-0.18499172,-0.16251886,-0.16251886,-0.12947905,-0.09798038,-0.07696104,-0.08994830,-0.09798050,-0.10594869,-0.12169695,-0.10764241,-0.08841109,-0.07231283,-0.06720877,-0.08406603,-0.07116926,-0.06782734,-0.02898753,-0.02898753,-0.03215718,-0.05715847,-0.04625905,-0.04373538,-0.05715847,-0.02565992,-0.01793778,-0.03138375,-0.02279091,-0.01745105,-0.00836837,-0.00836837,-0.00836837,0.01183438,0.00478530,0.02381063,0.00945628,0.00000000,0.00772190,0.01023304,0.02985287,0.00738001,0.00738001,0.01283383,0.01425588,0.01772630,0.01393747,0.01766038,0.00979578,0.01423144,0.01980257,0.03359580,0.05795431,0.07386971,0.06697214,0.08018970,0.06959331,0.05105507,0.02985299,0.04549563,0.05617034,0.06062460,0.07205331,0.06144726,0.06062472,0.07764351,0.07386971,0.08434105,0.09869826,0.09056854,0.07501328,0.09113336,0.08434117,0.09470403,0.10163271,0.09189916,0.11713076,0.09984541,0.10269022,0.11090827,0.11624765,0.12516308,0.13943100),
  yr_1 = c(-0.02864146,-0.05064440,-0.04715705,-0.02866817,-0.02775276,-0.04957283,-0.05565959,-0.02668774,-0.04757720,-0.03184420,-0.02262491,-0.03583831,-0.01764989,-0.00102872,0.02645826,0.00551271,-0.01249850,-0.02787292,-0.04469430,-0.03148317,-0.02615154,-0.01153111,-0.00974715,-0.02932584,-0.01696539,-0.01182616,0.01409030,0.00530624,-0.00663114,-0.02169991,-0.01509941,-0.01691270,-0.02761137,-0.00504899,-0.00962758,-0.01576924,-0.00702465,-0.00619400,0.00938773,0.00601268,-0.00808454,0.00575030,0.01329660,0.02769172,0.01254582,0.00000000,0.00803554,0.01316881,0.02574360,0.01221728,0.00285292,0.01057482,0.01085842,0.01350808,0.00822055,0.01331425,0.00367975,0.01084340,0.01445150,0.02639902,0.04926884,0.06333148,0.06118739,0.07654119,0.06544697,0.04704797,0.02919781,0.04483593,0.05142522,0.05785489,0.07158852,0.06071520,0.05840492,0.07782221,0.08402932,0.08309698,0.09613073,0.09737122,0.08145738,0.09734154,0.08897471,0.09928858,0.10806060,0.10086811,0.12250507,0.10675704,0.10917771,0.11496675,0.11794078,0.12540805,0.13208187),
  yr_2 = c(-0.17730552,-0.16857219,-0.14395398,-0.11679363,-0.10259151,-0.11264145,-0.11044610,-0.07156390,-0.08194947,-0.06080097,-0.04862267,-0.06134319,-0.04441774,-0.02739465,0.00442863,-0.01318312,-0.02811205,-0.04158711,-0.05738437,-0.04581630,-0.03932536,-0.02707887,-0.02459490,-0.04238999,-0.02806771,-0.02424562,0.00434756,-0.00575233,-0.01454222,-0.03153729,-0.02280521,-0.02581263,-0.03869367,-0.01315320,-0.01566899,-0.02322137,-0.01320481,-0.00950634,0.00216115,-0.00173354,-0.00611019,0.00418890,0.01003170,0.02643931,0.01092207,0.00000000,0.00893950,0.01410723,0.02709579,0.01060808,0.00426626,0.01032770,0.01165438,0.01441026,0.00828063,0.01157641,0.00243306,0.01376045,0.01640427,0.02548015,0.04784238,0.05440342,0.05768669,0.07267964,0.06057131,0.03971469,0.02446854,0.03305161,0.04085374,0.04615664,0.05452764,0.04268789,0.04404581,0.05161464,0.06235552,0.06100690,0.06635332,0.06911647,0.04609919,0.06149137,0.05420387,0.06150019,0.07111371,0.06369388,0.08403528,0.07254517,0.07630670,0.08599031,0.09360683,0.10352314,0.12207973),
  yr_3 = c(-0.16694885,-0.18823481,-0.18330753,-0.16574585,-0.15284240,-0.16713917,-0.16602337,-0.12707615,-0.13507187,-0.10870373,-0.09083533,-0.10030150,-0.07474267,-0.05585682,-0.02699292,-0.03514779,-0.05053473,-0.06584716,-0.07856345,-0.05919099,-0.05175662,-0.03582394,-0.03217340,-0.04459083,-0.03272486,-0.02749741,0.00293934,-0.00623322,-0.01626015,-0.02912664,-0.02174675,-0.02576554,-0.03728211,-0.01262593,-0.01166594,-0.02159190,-0.01056135,-0.01026571,0.00214851,-0.00298822,-0.00602734,0.00090170,0.00937963,0.02607870,0.00995195,0.00000000,0.00825512,0.01349068,0.02423394,0.01023114,0.00338686,0.00932229,0.01196182,0.01349676,0.00861263,0.01106834,0.00354922,0.01453626,0.01673901,0.02773917,0.04682505,0.05616581,0.05810702,0.07497251,0.05953968,0.04127812,0.02454174,0.03555429,0.04557741,0.05095208,0.05996847,0.04782712,0.04944253,0.05630672,0.06647372,0.06782699,0.06975579,0.07672179,0.05529976,0.07009542,0.05947196,0.07011962,0.07690752,0.07207775,0.09593415,0.07795691,0.08011532,0.07975912,0.08487654,0.08937478,0.09383988)
)

fig8b <- data.frame(
  p    = 5:95,
  yr_0 = c(-0.14310074,-0.08247614,-0.03649104,-0.07410800,-0.05129337,-0.02531767,-0.07410789,-0.07410789,-0.10227883,-0.08483195,-0.04779077,-0.06642544,-0.05921936,-0.02531779,-0.02531779,-0.05685472,-0.04512036,-0.02323663,-0.05063558,-0.03328598,-0.00751126,-0.02388823,-0.04705787,-0.05594397,-0.04933274,-0.02531779,-0.02531779,-0.00000012,0.03420818,0.00428271,-0.00956941,-0.02160716,-0.01526737,0.00453520,-0.00391865,-0.00729918,0.00672150,-0.01734960,-0.01304770,0.01390290,0.02542162,0.02193499,0.03922069,0.03922069,0.01550424,0.00000000,-0.00829172,0.00891531,0.00325799,0.01082122,0.02120233,0.02120233,0.03372478,0.03399861,0.03732646,0.03922069,0.03922069,0.03922069,0.05386293,0.04725301,0.03188765,0.03849375,0.05472481,0.05856359,0.06458652,0.06429446,0.07410800,0.06468523,0.06400526,0.07744181,0.09051406,0.08004272,0.07893217,0.08004272,0.08801091,0.08631241,0.07492745,0.08004272,0.09984529,0.12883294,0.13416183,0.11913025,0.12809241,0.13068640,0.14458120,0.10821354,0.13133585,0.13453090,0.17339838,0.17576611,0.13485110),
  yr_1 = c(-0.03243846,-0.00054729,0.01349139,-0.01269376,0.01196826,0.02674615,-0.01109004,-0.03206563,-0.06666958,-0.03745079,-0.02057207,-0.03586769,-0.02495170,0.00030243,-0.01463079,-0.03384221,-0.02181184,-0.01000416,-0.03614450,-0.02160501,-0.00002372,-0.01672184,-0.04364085,-0.05151343,-0.04172754,-0.02127552,-0.02430177,-0.00153720,0.02993941,0.00624645,-0.01050639,-0.02009392,-0.01259875,0.00061691,-0.00264275,-0.00637567,0.00777018,-0.00991905,-0.01575136,0.01000440,0.02375162,0.02975476,0.03799522,0.03462017,0.02146983,0.00000000,0.00157940,0.01434731,0.01118147,0.02211809,0.02887940,0.01941609,0.03890300,0.04544401,0.04483080,0.06198347,0.04969883,0.04093242,0.05943656,0.06753159,0.04950881,0.06080508,0.06588197,0.06130052,0.07882404,0.08623743,0.09680510,0.08320260,0.08929992,0.09575939,0.11415911,0.10193372,0.08836532,0.10258675,0.11225271,0.10959435,0.10667253,0.11853075,0.12357759,0.13675022,0.14899492,0.14749122,0.15076542,0.15467119,0.16601253,0.13217354,0.15172744,0.16645551,0.17995977,0.20244098,0.15896249),
  yr_2 = c(-0.07528007,-0.03433633,-0.00617015,-0.02859437,-0.00544250,0.01315534,-0.02417684,-0.04109895,-0.06834245,-0.04233134,-0.02231002,-0.03805029,-0.02426231,-0.00014448,-0.01301312,-0.03232312,-0.01890326,-0.00559688,-0.03074110,-0.01421666,0.00449038,-0.00929773,-0.03461123,-0.04529274,-0.03382897,-0.01315188,-0.01607704,0.00373387,0.03293335,0.01183856,-0.00504494,-0.01609850,-0.00723422,0.00599229,0.00165510,-0.00287890,0.00868499,-0.01570821,-0.01007473,0.01484001,0.02063620,0.02389777,0.04046154,0.03411007,0.01340997,0.00000000,-0.00914896,0.00580800,-0.00021052,0.00820589,0.02130353,0.01614654,0.02723801,0.02820766,0.03105915,0.03967786,0.03580618,0.03098631,0.04675126,0.04344201,0.02632427,0.03453088,0.04679132,0.04527402,0.05587578,0.05862832,0.06773162,0.05539131,0.05886555,0.06514597,0.08113122,0.07202840,0.06583452,0.07241654,0.07839441,0.07888126,0.07214689,0.07874990,0.09240723,0.11742759,0.12863374,0.11824083,0.12425494,0.12755132,0.14205599,0.10981226,0.13008976,0.13978601,0.16993546,0.18019128,0.14008975),
  yr_3 = c(-0.10240066,-0.05524409,-0.02946520,-0.05470967,-0.03435004,-0.01044738,-0.04746902,-0.06942642,-0.09144485,-0.06404090,-0.04594481,-0.05714595,-0.04701006,-0.02244198,-0.02750361,-0.05077565,-0.03713095,-0.02099741,-0.04279613,-0.02913296,-0.00623584,-0.02237165,-0.04746056,-0.05478847,-0.04470122,-0.02329957,-0.02468395,-0.00263977,0.02276158,0.00293875,-0.01312542,-0.02227044,-0.01242805,0.00068140,-0.00341034,-0.00694025,0.00511456,-0.01857257,-0.01164782,0.01314247,0.01543224,0.02350581,0.03997397,0.03032041,0.01257110,0.00000000,-0.00886393,0.00615978,-0.00106227,0.00867069,0.02192211,0.01658642,0.02796376,0.03083766,0.03329623,0.04437959,0.03973162,0.03597796,0.04903638,0.04795420,0.03131306,0.04138482,0.05451691,0.05067194,0.06150687,0.06544983,0.07558715,0.06335390,0.06799591,0.07509696,0.09215581,0.08131087,0.07451785,0.08107579,0.08834183,0.08608377,0.07647598,0.08691967,0.10081804,0.12708533,0.13307917,0.12482870,0.13053858,0.13164318,0.14566076,0.11601913,0.13384283,0.14263380,0.17044461,0.18840563,0.14675152)
)

# ── fig9: Actual vs counterfactual wage changes by percentile (female/male) ───
# fig9a = female, fig9b = male; period 1979–1989 for 9a, 1979–2024 for 9b

fig9a <- data.frame(
  p    = 5:95,
  yr_0 = c(-0.24456394,-0.18002546,-0.18002546,-0.17242742,-0.15330231,-0.11753511,-0.09614384,-0.10042048,-0.07242751,-0.05532193,-0.07082617,-0.07696116,-0.10113144,-0.09132469,-0.08289862,-0.04962397,-0.06942666,-0.05076611,-0.04841256,-0.03160548,-0.04485071,-0.07082617,-0.05532193,-0.05532193,-0.01610124,-0.02852380,-0.02518487,-0.02237785,-0.00261796,-0.02817106,-0.04735386,-0.03160548,-0.01098621,-0.01493394,-0.03730345,-0.03944874,-0.03511918,-0.03160548,-0.03160548,-0.03160548,-0.00913262,0.00921655,0.00084829,-0.00227773,-0.00590646,0.00000000,-0.00913250,-0.01142514,0.00027668,0.00048280,0.00495207,0.00921667,0.00921667,0.00588882,-0.02357328,-0.01671696,0.01049566,0.00067127,0.01535141,0.00166941,-0.00320601,-0.00385559,-0.00170004,0.02691615,0.01898634,0.00229609,0.00787330,0.00921655,0.00921655,0.02344728,0.00537777,0.00921655,0.03634524,0.04250264,0.02277136,0.03247333,0.04888177,0.03738737,0.01254439,0.05003858,0.04419613,0.04030728,0.03887439,0.04651213,0.07612729,0.08248878,0.07977319,0.09169269,0.05177617,0.08717799,0.09193873),
  yr_1 = c(-0.06078869,-0.02888799,-0.05850571,-0.05339146,-0.03951728,-0.02200216,-0.01723099,-0.01717579,0.00481260,0.01902759,-0.00120425,-0.02174711,-0.04445517,-0.03555501,-0.02956831,-0.00829089,-0.02915835,-0.01095068,-0.00627136,-0.00031638,-0.01813900,-0.04417431,-0.02379537,-0.03128541,-0.00090528,-0.01024437,-0.00977528,-0.00788820,0.00399005,-0.01697373,-0.03811121,-0.02181542,-0.01258445,-0.01059651,-0.03480899,-0.03615832,-0.03510571,-0.02743971,-0.03001654,-0.03216887,-0.01423931,-0.00097883,-0.00116527,-0.00303555,-0.00823319,0.00000000,-0.01321912,-0.01384246,-0.00282717,-0.00512266,0.00519514,0.00926578,0.00341642,0.00117207,-0.01913106,-0.02172852,0.00381076,0.00345886,0.01008725,0.00810492,0.00186157,0.00061429,0.00562346,0.02338350,0.02963042,0.00897610,0.02322257,0.01724195,0.00866127,0.03863668,0.01831579,0.02776289,0.04283857,0.05345821,0.04173398,0.05155635,0.06767344,0.05048561,0.03949499,0.05788779,0.06373048,0.05862260,0.05981135,0.06856918,0.08575416,0.09797764,0.09409881,0.10082603,0.06228018,0.09033728,0.09590816),
  yr_2 = c(-0.12443084,-0.08540624,-0.10059136,-0.09247780,-0.06788337,-0.04652202,-0.04252183,-0.03499126,-0.00972652,0.00519276,-0.01082718,-0.03197873,-0.05504000,-0.04341590,-0.03774285,-0.01401901,-0.03247046,-0.01636696,-0.01073456,-0.00503516,-0.01819253,-0.04694641,-0.02803314,-0.03429604,-0.00105560,-0.01109791,-0.01156044,-0.00797951,0.00394797,-0.01638329,-0.03625572,-0.02061570,-0.00921857,-0.00940037,-0.03143787,-0.03311241,-0.03293705,-0.02543700,-0.02815568,-0.03078914,-0.01087415,0.00119460,0.00005817,-0.00159061,-0.00724924,0.00000000,-0.01116812,-0.01415622,-0.00539041,-0.00497401,0.00183451,0.00789607,0.00445747,-0.00371587,-0.02821088,-0.02108824,-0.00053942,-0.00546563,0.00806355,-0.00323188,-0.01104927,-0.01252556,-0.00744474,0.01634526,0.01115930,-0.00821495,-0.00083554,0.00077021,-0.00359952,0.01495230,-0.00543201,0.00206530,0.02349102,0.03039205,0.01351798,0.02285945,0.03845203,0.02215588,0.00523484,0.03544366,0.03543007,0.03272188,0.03688204,0.03920186,0.06276143,0.08034909,0.07706153,0.08792007,0.05290258,0.08423483,0.09314501),
  yr_3 = c(-0.16233736,-0.12098932,-0.13696253,-0.12868428,-0.10506546,-0.08035398,-0.07138360,-0.06463575,-0.04109907,-0.01843357,-0.04149592,-0.05980718,-0.08125949,-0.06832826,-0.05908716,-0.03997386,-0.05064654,-0.03413510,-0.02582800,-0.02039254,-0.03554201,-0.05981064,-0.03940213,-0.04607987,-0.01229489,-0.02133417,-0.01896906,-0.01577997,-0.00576985,-0.02411497,-0.04421544,-0.02916062,-0.01603949,-0.01543868,-0.03695023,-0.03893197,-0.03780854,-0.02620578,-0.03164327,-0.03403521,-0.01413178,-0.00080431,-0.00394225,-0.00284171,-0.00759137,0.00000000,-0.01283967,-0.01424885,-0.00608182,-0.00571620,0.00246334,0.00938678,0.00415361,-0.00485289,-0.02907813,-0.02119863,-0.00160336,-0.00728905,0.00902236,-0.00346100,-0.01101720,-0.01226735,-0.00614452,0.01811254,0.01311457,-0.00567186,0.00426245,0.00312853,-0.00189996,0.01627231,-0.00229907,0.00713563,0.02793336,0.03493977,0.01854229,0.02739120,0.04187274,0.02660251,0.01045370,0.03728056,0.03793097,0.03479147,0.03551340,0.04367876,0.06766629,0.07493997,0.07397962,0.08606100,0.04832983,0.08209229,0.08665633)
)

fig9b <- data.frame(
  p    = 5:95,
  yr_0 = c(-0.20981491,-0.17423356,-0.12291396,-0.09620690,-0.06323397,-0.03586280,-0.00812614,-0.01447165,-0.02789474,-0.02529407,-0.00257695,-0.00871193,-0.00471139,-0.01053429,-0.01606023,0.00143278,-0.00687528,-0.00086594,-0.02789474,-0.01350594,-0.00120723,-0.01304829,-0.02616000,-0.01784444,0.01292729,0.00050473,-0.02147412,-0.03118956,-0.00847673,-0.02446020,-0.02130723,-0.02481318,-0.00954556,-0.01293409,-0.02034760,-0.02630091,-0.02874529,-0.02789474,-0.02581358,-0.00542188,0.01292729,0.01292729,0.00062966,0.00335777,0.00539434,0.00000000,0.00684822,0.01203072,0.01265275,0.01626086,-0.00510657,-0.00105894,0.01292741,0.02064931,0.02095950,0.01292729,0.03664374,0.03349364,0.04819548,0.03523302,0.03780031,0.03094590,0.04109824,0.05438387,0.06351912,0.06880772,0.04593349,0.06488705,0.08988833,0.08517241,0.09503102,0.09104514,0.11672401,0.13173556,0.13337350,0.13462424,0.12405133,0.14645863,0.14460492,0.17655659,0.18403912,0.19853282,0.17593074,0.19524884,0.23607087,0.24654222,0.25533438,0.27772498,0.25433755,0.27529168,0.33674836),
  yr_1 = c(-0.06045586,-0.03916335,-0.02018780,-0.00311112,0.01176822,0.02032036,0.03571820,0.03691173,0.03811228,0.03840411,0.03390145,0.03282189,0.03185523,0.01821995,0.02082419,0.02689791,0.02022088,0.01401758,0.00586295,0.01069689,0.00735986,-0.00230753,-0.00585604,0.00050843,0.00119507,0.00572884,-0.00472772,-0.01667750,-0.01291466,-0.01325333,-0.01960719,-0.01637471,-0.01082098,-0.01708055,-0.02355063,-0.02392173,-0.03247714,-0.03047597,-0.02135217,-0.00642657,0.00361443,0.00685298,-0.00178349,0.00326943,0.00339544,0.00000000,0.00438905,0.01124465,0.01154304,0.01319456,0.00214410,0.00072968,0.01084173,0.02066803,0.02747595,0.01716042,0.03618157,0.04006708,0.04627347,0.04537046,0.04939079,0.04463327,0.05040038,0.05081403,0.07559514,0.07432425,0.06561363,0.07501674,0.08738446,0.10060787,0.10431623,0.10920787,0.11836123,0.13637137,0.14355922,0.14530945,0.14086270,0.15052605,0.16289878,0.17459178,0.18968630,0.19870543,0.19089150,0.20245099,0.22892118,0.24598312,0.26131582,0.26570296,0.26021385,0.27290010,0.32435417),
  yr_2 = c(-0.08815426,-0.07284611,-0.04772872,-0.02837849,-0.00314033,0.00683832,0.01882875,0.02960336,0.03085804,0.03111959,0.02930701,0.02919161,0.02651560,0.01749945,0.01776803,0.02749169,0.02173173,0.01371539,0.00604510,0.01096082,0.01082683,-0.00146186,-0.00687277,0.00309515,0.00657415,0.00774157,-0.00501895,-0.01609242,-0.00939167,-0.01066041,-0.01645064,-0.01269352,-0.00708055,-0.01492047,-0.01863790,-0.02057135,-0.03016329,-0.02865303,-0.01935565,-0.00478911,0.00795639,0.00925386,-0.00083518,0.00490344,0.00446737,0.00000000,0.00522482,0.00994694,0.00737667,0.01278603,-0.00387561,-0.00211108,0.01089191,0.01247728,0.01641726,0.01367342,0.03037107,0.02942693,0.04226637,0.03136337,0.03308511,0.02965379,0.03734004,0.04266787,0.05626571,0.05822945,0.04329669,0.05988824,0.07791746,0.07956207,0.08544314,0.08885324,0.10607779,0.11964023,0.12590015,0.12708914,0.12053883,0.13349712,0.14096320,0.16573584,0.17511690,0.18443501,0.18422163,0.19301617,0.22491586,0.24619520,0.25965297,0.27236521,0.26024354,0.27203977,0.33044851),
  yr_3 = c(-0.12732941,-0.10728908,-0.08240473,-0.05968690,-0.03266680,-0.01545107,-0.00445926,0.00443590,0.00456405,-0.00034022,0.00310051,0.00873458,0.00428629,-0.00103879,0.00202346,0.00183392,0.00665009,-0.00037420,-0.00880778,-0.00979936,-0.00616026,-0.01318979,-0.01851690,-0.01238036,0.00119591,0.00274694,-0.01452541,-0.02287889,-0.01573706,-0.01430249,-0.01951396,-0.01704562,-0.00939345,-0.01728714,-0.02155387,-0.02254665,-0.03060210,-0.02200317,-0.02021563,-0.00413775,0.01043010,0.00981176,-0.00035787,0.00562000,0.00719130,0.00000000,0.00514662,0.01001740,0.00654292,0.01292312,-0.00064278,0.00041747,0.01207960,0.01386750,0.01610696,0.01925528,0.03364253,0.03221071,0.04610431,0.03795207,0.03860533,0.03671622,0.04313803,0.05275261,0.06371629,0.06849492,0.05541587,0.06954002,0.08595109,0.08864594,0.09447002,0.09802938,0.11496401,0.13056135,0.13749743,0.13685608,0.13124633,0.14351153,0.15218639,0.17411947,0.18549562,0.19795632,0.18190694,0.19985485,0.23332119,0.24674940,0.26300359,0.27669215,0.26216102,0.27406335,0.33186245)
)


# =============================================================================
# FIGURE 6 HELPER — state-level scatter with linear fit
# =============================================================================

make_fig6 <- function(df, ytitle_text, xtitle_text) {
  ggplot(df, aes(x = x, y = y)) +
    geom_text(aes(label = abbrev), color = "#8B1A1A", size = 2.5) +
    geom_smooth(method = "lm", se = FALSE, color = "#0000CD",
                linewidth = 0.9, linetype = "solid") +
    labs(x = xtitle_text, y = ytitle_text) +
    stata_theme +
    theme(legend.position = "none")
}

fig6a_all_plot <- make_fig6(fig6a_all,
  ytitle_text = "Mean log(p60)\u2013log(p40), 1979\u20132024",
  xtitle_text = "Mean log(p50), 1979\u20132024")

fig6a_f_plot <- make_fig6(fig6a_f,
  ytitle_text = "Mean log(p60)\u2013log(p40), 1979\u20132024",
  xtitle_text = "Mean log(p50), 1979\u20132024")

fig6a_m_plot <- make_fig6(fig6a_m,
  ytitle_text = "Mean log(p60)\u2013log(p40), 1979\u20132024",
  xtitle_text = "Mean log(p50), 1979\u20132024")

fig6b_all_plot <- make_fig6(fig6b_all,
  ytitle_text = "Trend log(p60)\u2013log(p40), 1979\u20132012",
  xtitle_text = "Trend log(p50), 1979\u20132012")

fig6b_f_plot <- make_fig6(fig6b_f,
  ytitle_text = "Trend log(p60)\u2013log(p40), 1979\u20132012",
  xtitle_text = "Trend log(p50), 1979\u20132012")

fig6b_m_plot <- make_fig6(fig6b_m,
  ytitle_text = "Trend log(p60)\u2013log(p40), 1979\u20132012",
  xtitle_text = "Trend log(p50), 1979\u20132012")


# =============================================================================
# FIGURE 8 / 9 HELPER — actual vs counterfactual wage changes by percentile
# =============================================================================

make_fig89 <- function(df, ytitle_text) {
  ggplot(df, aes(x = p)) +
    geom_line(aes(y = yr_0, color = "Actual change",
                  linetype = "Actual change"), linewidth = 0.8) +
    geom_point(aes(y = yr_0, color = "Actual change"), shape = 15, size = 1.2) +
    geom_line(aes(y = yr_1, color = "Cntfct.: no state FE",
                  linetype = "Cntfct.: no state FE"), linewidth = 0.8) +
    geom_point(aes(y = yr_1, color = "Cntfct.: no state FE"), shape = 17, size = 1.0) +
    geom_line(aes(y = yr_2, color = "Cntfct.: state time trends",
                  linetype = "Cntfct.: state time trends"), linewidth = 0.8) +
    geom_point(aes(y = yr_2, color = "Cntfct.: state time trends"), shape = 4, size = 1.2) +
    geom_line(aes(y = yr_3, color = "Cntfct.: FD",
                  linetype = "Cntfct.: FD"), linewidth = 0.8) +
    geom_point(aes(y = yr_3, color = "Cntfct.: FD"), shape = 16, size = 1.0) +
    geom_hline(yintercept = 0, linewidth = 0.4, color = "black") +
    scale_x_continuous(
      name   = "Percentile",
      breaks = seq(0, 100, 5),
      limits = c(5, 95)
    ) +
    scale_y_continuous(
      name   = ytitle_text,
      labels = number_format(accuracy = 0.1)
    ) +
    scale_color_manual(
      name = NULL,
      values = c(
        "Actual change"             = "black",
        "Cntfct.: no state FE"      = "#8B1A1A",
        "Cntfct.: state time trends"= "#228B22",
        "Cntfct.: FD"               = "#1F3E6E"
      )
    ) +
    scale_linetype_manual(
      name = NULL,
      values = c(
        "Actual change"             = "solid",
        "Cntfct.: no state FE"      = "solid",
        "Cntfct.: state time trends"= "solid",
        "Cntfct.: FD"               = "solid"
      )
    ) +
    guides(color = guide_legend(nrow = 2), linetype = guide_legend(nrow = 2)) +
    stata_theme

}

fig8a_plot <- make_fig89(fig8a, "Change in log(p)\u2013log(p50), 1979\u20131989")
fig8b_plot <- make_fig89(fig8b, "Change in log(p)\u2013log(p50), 1979\u20131989")
fig9a_plot <- make_fig89(fig9a, "Change in log(p)\u2013log(p50), 1979\u20131989")
fig9b_plot <- make_fig89(fig9b, "Change in log(p)\u2013log(p50), 1979\u20132024")

```
\ 
Figure 1B:

```{r,echo=FALSE,message=FALSE,warning=FALSE}
fig1b_plot
```
\ 
Figure 2:

```{r,message=FALSE,warning=FALSE,echo=FALSE}
fig2_plot
```
\ 
Figure 3 Male:

```{r,message=FALSE,warning=FALSE,echo=FALSE}
fig3_m_plot
```
\ 
Figure 3 Female:

```{r,message=FALSE,warning=FALSE,echo=FALSE}
fig3_f_plot
```
\ 
Figure 3 Pooled:

```{r,message=FALSE,warning=FALSE,echo=FALSE}
fig3_all_plot
```
\ 
Figure 4 M LVL:

```{r,message=FALSE,warning=FALSE,echo=FALSE}
fig4_m_lvl_plot
```
\ 
Figure 4 M FD:

```{r,message=FALSE,warning=FALSE,echo=FALSE}
fig4_m_lvl_plot
```
\ 
Figure 4 F LVL:

```{r,message=FALSE,warning=FALSE,echo=FALSE}
fig4_f_lvl_plot
```
\ 
Figure 4 F FD:

```{r,message=FALSE,warning=FALSE,echo=FALSE}
fig4_f_fd_plot
```
\ 
Figure 4 Pooled LVL::

```{r,message=FALSE,warning=FALSE,echo=FALSE}
fig4_all_lvl_plot
```
\ 
Figure 4 Pooled FD:

```{r,message=FALSE,warning=FALSE,echo=FALSE}
fig4_all_fd_plot
```
\ 
Figure 5 Pooled:

```{r,message=FALSE,warning=FALSE,echo=FALSE}
fig5_all_plot
```
\ 
Figure 5 M:

```{r,message=FALSE,warning=FALSE,echo=FALSE}
fig5_m_plot
```
\ 
Figure 5 F:

```{r,message=FALSE,warning=FALSE,echo=FALSE}
fig5_f_plot
```
\ 
Figure 6A Pooled:

```{r,echo=FALSE,warning=FALSE,message=FALSE}
fig6a_all_plot
```
\ 
Figure 6A M:

```{r,echo=FALSE,warning=FALSE,message=FALSE}
fig6a_m_plot
```
\ 
Figure 6A F:

```{r,echo=FALSE,warning=FALSE,message=FALSE}
fig6a_f_plot
```
\ 
Figure 6B Pooled:

```{r,echo=FALSE,warning=FALSE,message=FALSE}
fig6b_all_plot
```
\ 
Figure 6B M:

```{r,echo=FALSE,warning=FALSE,message=FALSE}
fig6b_m_plot
```
\ 
Figure 6B F:

```{r,echo=FALSE,warning=FALSE,message=FALSE}
fig6b_f_plot
```
\ 
Figure 8A:

```{r,echo=FALSE,warning=FALSE,message=FALSE}
fig8a_plot
```
\ 
Figure 8B:

```{r,echo=FALSE,warning=FALSE,message=FALSE}
fig8b_plot
```
\ 
Figure 9A:

```{r,echo=FALSE,warning=FALSE,message=FALSE}
fig9a_plot
```
\ 
Figure 9B:

```{r,echo=FALSE,warning=FALSE,message=FALSE}
fig9b_plot
```
\ 
Table 1:
```{r,echo=FALSE,message=FALSE,warning=FALSE, results='asis'}
# =============================================================================
# R Code to Render Table 1 in a Quarto PDF Document
# One table: Year | States | Female (4) | Male (4) | Pooled (4)
# Note emitted outside the scaled box so only the data grid shrinks.
# =============================================================================

library(knitr)
library(kableExtra)

# ── Data ─────────────────────────────────────────────────────────────────────
table1 <- data.frame(
  year      = c(1979,1980,1981,1982,1983,1984,1985,1986,1987,1988,1989,1990,
                1991,1992,1993,1994,1995,1996,1997,1998,1999,2000,2001,2002,
                2003,2004,2005,2006,2007,2008,2009,2010,2011,2012,2013,2014,
                2015,2016,2017,2018,2019,2020,2021,2022,2023,2024),
  statebind = c(1,1,1,1,1,1,2,5,6,10,12,11,4,7,7,8,9,11,10,7,10,10,10,11,
                11,12,15,19,30,31,26,15,19,17,18,21,27,27,28,28,28,29,30,30,30,31),
  c2_f      = c(5.0,6.0,5.0,5.0,3.5,2.5,2.0,2.0,2.0,2.0,1.0,1.5,1.5,2.0,
                2.5,2.5,2.0,2.0,2.5,2.5,2.5,2.0,2.0,1.5,1.5,1.5,1.5,1.5,
                1.5,2.0,2.5,3.5,3.0,2.5,2.0,2.0,1.5,1.5,1.5,1.5,1.5,1.0,
                1.0,1.0,1.0,1.0),
  c3_f      = c(28.0,24.0,24.0,21.5,17.5,15.5,14.5,16.0,14.0,12.5,12.5,14.0,
                18.5,14.0,11.0,11.0,9.5,12.5,14.5,11.5,11.0,9.5,9.0,9.0,9.0,
                7.5,8.5,9.5,10.0,13.0,10.5,9.5,10.5,12.0,11.5,13.5,12.0,15.0,
                15.5,14.0,20.0,15.5,11.5,11.5,13.5,13.5),
  c4_f      = c(0.1275,0.1324,0.1308,0.1063,0.0981,0.0891,0.0800,0.0717,0.0635,
                0.0593,0.0537,0.0538,0.0697,0.0651,0.0577,0.0579,0.0518,0.0491,
                0.0635,0.0648,0.0536,0.0484,0.0454,0.0429,0.0398,0.0392,0.0416,
                0.0408,0.0530,0.0559,0.0619,0.0616,0.0595,0.0761,0.0708,0.0719,
                0.0768,0.0765,0.0735,0.0748,0.0859,0.0666,0.0670,0.0614,0.0683,0.0671),
  c5_f      = c(-0.3815,-0.4013,-0.4147,-0.4798,-0.5108,-0.5444,-0.5641,-0.5943,
                -0.6039,-0.6024,-0.6122,-0.5844,-0.5812,-0.5813,-0.5893,-0.6051,
                -0.6068,-0.6140,-0.6007,-0.5796,-0.5779,-0.5908,-0.5929,-0.5971,
                -0.6131,-0.6277,-0.6406,-0.6374,-0.6308,-0.6361,-0.6422,-0.6395,
                -0.6460,-0.6934,-0.6867,-0.6815,-0.6794,-0.6637,-0.6634,-0.6460,
                -0.6538,-0.6682,-0.6473,-0.6145,-0.6079,-0.6098),
  c2_m      = c(2.0,2.5,1.5,2.0,2.0,1.5,1.0,1.0,1.0,1.0,1.0,0.5,0.5,1.0,1.0,
                1.0,0.5,1.0,1.0,1.0,1.0,1.0,0.5,1.0,0.5,1.0,1.0,0.5,0.5,1.0,
                1.0,2.0,1.5,1.5,1.0,1.5,1.5,1.0,1.5,0.5,0.5,0.5,0.5,0.5,0.5,0.5),
  c3_m      = c(10.5,10.0,9.0,8.0,8.0,7.5,6.5,6.5,6.0,6.0,5.0,6.0,9.0,6.5,5.0,
                4.5,4.5,7.0,7.5,7.0,5.5,6.0,5.5,6.0,5.0,5.0,5.0,6.0,6.0,6.5,
                6.0,6.5,8.0,7.5,8.0,10.0,7.5,11.5,12.0,9.5,13.0,10.0,8.0,8.0,
                10.5,10.0),
  c4_m      = c(0.0466,0.0555,0.0557,0.0496,0.0483,0.0412,0.0373,0.0334,0.0306,
                0.0289,0.0277,0.0282,0.0378,0.0362,0.0344,0.0315,0.0279,0.0285,
                0.0375,0.0390,0.0308,0.0282,0.0280,0.0280,0.0259,0.0251,0.0249,
                0.0249,0.0325,0.0357,0.0421,0.0428,0.0397,0.0514,0.0474,0.0544,
                0.0514,0.0549,0.0507,0.0522,0.0575,0.0431,0.0476,0.0443,0.0488,0.0488),
  c5_m      = c(-0.6355,-0.6519,-0.6841,-0.7135,-0.7285,-0.7286,-0.7369,-0.7444,
                -0.7294,-0.7154,-0.7210,-0.7188,-0.7122,-0.7194,-0.7269,-0.7128,
                -0.7057,-0.7087,-0.6856,-0.6882,-0.6858,-0.6771,-0.6845,-0.6947,
                -0.6940,-0.7015,-0.7079,-0.6989,-0.7037,-0.7068,-0.7364,-0.7290,
                -0.7229,-0.7745,-0.7639,-0.7507,-0.7573,-0.7411,-0.7282,-0.7199,
                -0.7169,-0.7237,-0.6862,-0.6572,-0.6500,-0.6630),
  c2_all    = c(3.5,4.0,2.5,3.5,3.0,2.0,1.5,1.5,1.5,1.5,1.0,1.0,1.0,1.5,1.5,
                2.0,1.5,1.5,1.5,2.0,2.0,1.5,1.5,1.5,1.5,1.5,1.5,1.0,1.5,1.0,
                2.0,3.0,2.5,2.0,1.5,2.0,1.5,1.5,1.5,1.0,1.0,1.0,1.0,0.5,0.5,1.0),
  c3_all    = c(17.0,15.5,14.5,12.5,11.5,10.5,9.5,10.0,9.0,8.0,7.0,9.0,12.5,
                9.5,7.5,7.5,6.0,9.5,10.0,8.0,7.0,7.5,7.0,7.5,6.5,6.0,6.5,7.5,
                7.5,8.5,8.0,7.5,9.0,9.5,9.5,11.5,9.5,13.0,13.5,11.5,16.0,12.5,
                9.5,9.5,11.5,11.5),
  c4_all    = c(0.0780,0.0861,0.0859,0.0728,0.0689,0.0609,0.0550,0.0495,0.0445,
                0.0418,0.0388,0.0392,0.0516,0.0488,0.0446,0.0429,0.0382,0.0374,
                0.0489,0.0502,0.0408,0.0370,0.0356,0.0346,0.0321,0.0313,0.0323,
                0.0319,0.0416,0.0447,0.0511,0.0513,0.0486,0.0625,0.0579,0.0623,
                0.0628,0.0645,0.0609,0.0624,0.0703,0.0537,0.0565,0.0520,0.0577,0.0571),
  c5_all    = c(-0.5793,-0.5879,-0.5995,-0.6252,-0.6518,-0.6721,-0.6871,-0.6981,
                -0.7019,-0.6858,-0.6814,-0.6675,-0.6707,-0.6697,-0.6758,-0.6858,
                -0.6850,-0.6711,-0.6581,-0.6497,-0.6501,-0.6493,-0.6605,-0.6526,
                -0.6639,-0.6773,-0.6791,-0.6785,-0.6826,-0.6888,-0.7069,-0.7007,
                -0.6934,-0.7404,-0.7302,-0.7236,-0.7296,-0.7088,-0.7044,-0.6873,
                -0.6942,-0.7001,-0.6642,-0.6386,-0.6384,-0.6390),
  stringsAsFactors = FALSE
)

# ── Format columns ────────────────────────────────────────────────────────────
fmt1 <- function(x) formatC(x, format = "f", digits = 1)
fmt3 <- function(x) formatC(x, format = "f", digits = 3)

display <- data.frame(
  Year    = table1$year,
  SB      = as.integer(table1$statebind),
  F_c2    = fmt1(table1$c2_f),
  F_c3    = fmt1(table1$c3_f),
  F_share = fmt3(table1$c4_f),
  F_lp    = fmt3(table1$c5_f),
  M_c2    = fmt1(table1$c2_m),
  M_c3    = fmt1(table1$c3_m),
  M_share = fmt3(table1$c4_m),
  M_lp    = fmt3(table1$c5_m),
  A_c2    = fmt1(table1$c2_all),
  A_c3    = fmt1(table1$c3_all),
  A_share = fmt3(table1$c4_all),
  A_lp    = fmt3(table1$c5_all),
  stringsAsFactors = FALSE
)

# ── Render table (no footnote inside — note goes below as plain text) ─────────
kbl(
  display,
  format    = "latex",
  booktabs  = TRUE,
  longtable = FALSE,
  linesep   = "",
  align     = rep("r", 14),
  col.names = c(
    "Year", "(1)",
    "(2)", "(3)", "Share", "log(p50/p10)",
    "(2)", "(3)", "Share", "log(p50/p10)",
    "(2)", "(3)", "Share", "log(p50/p10)"
  ),
  escape  = FALSE,
  caption = "TABLE 1: Minimum Wage Bindingness and Wage Distribution, 1979--2024",
  label   = "tab:table1"
) |>
  kable_styling(
    latex_options = c("HOLD_position", "scale_down"),
    full_width    = FALSE
  ) |>
  add_header_above(c(
    " "        = 2,
    "Female"   = 4,
    "Male"     = 4,
    "Pooled"   = 4
  ))

# Note lives outside the resizebox so it renders at normal size
cat(paste0(
  "\\begin{minipage}{\\linewidth}\\vspace{4pt}\\footnotesize\n",
  "\\textit{Notes:} ",
  "(1)~=~states bound by federal minimum; ",
  "(2)~=~mean share of workers at or below minimum; ",
  "(3)~=~weighted states with binding state minimum. ",
  "log(p50/p10)~=~mean log(p50)$-$log(p10).\n",
  "\\end{minipage}\n"
))
```


\newpage

## References
